---
title: "60HN - ASPARNet study - CRE Admission Risk: Datasets, Variables and Models"
author: "Vu Thi Lan Huong"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_depth: 2
    number_sections: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document: default
editor_options: 
  chunk_output_type: console
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Packages

```{r packages}
library(dplyr)
library(purrr)
library(tidyr)
library(stringr)
library(magrittr)
library(readxl)
library(gmodels)
library(lsmeans)
library(lme4)
library(glmmLasso)
```


# Constants

```{r constants}
if (grepl("arc|hoisy", Sys.getenv("USER"))) {
  path2data <- paste0("~/Library/CloudStorage/OneDrive-OxfordUniversityClinical",
                      "ResearchUnit/GitHub/HuongVTL/CRE-gut-acquisition/")
} else {
  path2data <- paste("C:/Users/huongvtl/OneDrive - Oxford University Clinical",
                     "Research Unit/60HN CRE transmission manuscript/")
}
```


# Functions

```{r}
"%ni%" <- Negate("%in%")
```

```{r}
make_path <- function(file) paste0(path2data, file)
```

Tuning `read_excel()`:

```{r}
read_excel2 <- function(file, ...) read_excel(make_path(file), ...)
```

Tuning `excel_sheets()`:

```{r}
excel_sheets2 <- function(file) excel_sheets(make_path(file))
```

A function that reads all the sheets of an excel file:

``` {r}
readxl_allsheet <- function(filename, tibble = FALSE) {
  # I prefer straight data.frames
  # but if you like tidyverse tibbles (the default with read_excel)
  # then just pass tibble = TRUE
  sheets <- c("SCR", "ADM", "DEMO_HIS", "DEMO_HIS_HISTORY_GRID", "DIS", "ANT",
              "ANT_ANB_HOSP_GRID")
#  sheets <- filename |>
#    excel_sheets2() |> 
#    setdiff("Category")
  x <- lapply(sheets, function(X) {
    filename |>
      read_excel2(sheet = X) |> 
      filter(entry == 2)
  })
  if(!tibble) x <- lapply(x, as.data.frame)
  names(x) <- sheets
  x
}
```

```{r}
merge2 <- function(...) merge(..., by = "USUBJID", all = TRUE)
```


# Datasets and variables

## Source data

The list of non-CRE bacteria to exclude from the data:

```{r}
non_CRE <- c("Acinetobacter baumannii", "Aeromonas caviae", "Aeromonas hydrophila",
             "Aeromonas veronii", "Enterococcus faecium", "Cupriavidus gilardii",
             "Pseudomonas putida")
```

Reading the data sets:

```{r load data}
survey <- readxl_allsheet("16-12-2025-_60HN_PATIENT_P1_Data.xls")
cre <- read_excel2("60HN_ID_MALDITOF_confirmation_20251128.xlsx") |> 
  filter(Identification_MALDITOF %ni% non_CRE) |> 
  mutate(hospitaltype = ifelse(SiteID %in% c("010","159"), 1, 2))
```

```{r}
discharge_date <- "60HN - DischargeDate_no_discharge_sample_27Nov25.xlsx" |>
  read_excel2() |> 
  select(USUBJID, `Discharge date`)
```


## CRE datasets

```{r}
remove_duplicates <- function(x) {
  x |>
    select(USUBJID, SPEC_DATE) |> 
    unique()
}
```

```{r cre carriage and species}
CRE_admission <- subset(cre, cre$SampleSchedule == "ADMISSION"); 
CRE_discharge <- subset(cre, cre$SampleSchedule == "DISCHARGE")

length(unique(CRE_admission$USUBJID))
length(unique(CRE_discharge$USUBJID))

## subset to specific CREC or CRKP
CREC_admission <- CRE_admission %>%
  filter(Identification_MALDITOF == "Escherichia coli") %>%
  remove_duplicates()

CREC_discharge <- CRE_discharge %>%
  filter(Identification_MALDITOF == "Escherichia coli") %>%
  remove_duplicates()

CRKP_admission <- CRE_admission %>%
  filter(Identification_MALDITOF == "Klebsiella pneumoniae") %>%
  remove_duplicates()

CRKP_discharge <- CRE_discharge %>%
  filter(Identification_MALDITOF == "Klebsiella pneumoniae") %>%
  remove_duplicates()
```

## Survey data set

```{r}
survey$SCR <- survey$SCR |> 
  select(USUBJID, SPEC_DATE_DISCHARGE) |> 
  left_join(discharge_date, "USUBJID") |> 
  mutate(DISCHARGE_DATE = coalesce(SPEC_DATE_DISCHARGE, `Discharge date`)) |>
  select(USUBJID, DISCHARGE_DATE)

survey$ADM <- survey$ADM |> 
  select(USUBJID, SITEID, YEAR_BIRTH, GENDER, ADMISSION_DATE, WARD_3, CORMOBIDITY,
         MI_HIS, CHF, PVD, CVD, DEMENTIA, CPD, CTD, PUD, MILD_LIVER, SEV_LIVER,
         HEMIPLEGIA, SEV_RENAL, starts_with("DIAB"), TUMOR_NOMETA, LEUKEMIA, LYMPHOMA,
         META_TUMOR, ANB_ADMISSION) |> 
  mutate(hospitaltype = ifelse(SITEID %in% c("010", "159"), 1, 2),
         age = 2025 - YEAR_BIRTH + 1,
         Ab_history = ifelse(ANB_ADMISSION %in% c(1, 4), 0, 1),
         wardtype = ifelse(WARD_3 == 1, "surgical", "medical/ID")) |> 
  select(-YEAR_BIRTH, -ANB_ADMISSION, -WARD_3)

admission <- survey |> 
  extract(c("SCR", "ADM")) |> 
  reduce(merge2) |> 
  mutate(los = as.numeric((as.POSIXct(DISCHARGE_DATE) -
                             as.POSIXct(ADMISSION_DATE)) / 86400 + 1)) |>
  select(-DISCHARGE_DATE, -ADMISSION_DATE)
```

```{r}
survey$DEMO_HIS <- survey$DEMO_HIS |> 
  select(USUBJID, MARITAL, starts_with("JOB"), ADULT, CHILDREN, AMBULATORY, SMOKING,
         starts_with("ALCOHOL"), starts_with("DRUG")) |> 
  mutate(job = JOB_SPECIFY |>
           case_match(c("Cán bộ công chức", "Cán bộ xã") ~ 1,
                      c("Bảo vệ", "Cơ khí","Hộ lý", "Lái tàu thủy", "Lao động tự do",
                        "Vệ sỹ") ~ 4,
                      c("già", "Già", "Hết độ tuổi lao động") ~ 8,
                      c("Ở nhà", "Tự do") ~ 9, .default = as.numeric(JOB)) |> 
           case_match(6 ~ "farmer", 7 ~ "housewife", 8 ~ "retired",
                      .default = "all other jobs"),
         householdsize = ADULT + CHILDREN,
         smoking = case_match(SMOKING, "1" ~ "current smoker",
                                       "2" ~ "former smoker",
                                       .default = "all non-smokers"),
         children = ifelse(CHILDREN < 1, "no children in the household",
                                         "with children in the household"),
         married = ifelse(MARITAL == 1, "married", "other"),
         ambulatory = ifelse(AMBULATORY == 1, "independent", "not independent"),
         across(starts_with(c("ALCOHOL", "DRUG")), as.integer),
         alcohol = ifelse(ALCOHOL_CUTDOWN + ALCOHOL_ANNOYED + ALCOHOL_GUILTY +
                            ALCOHOL_DRUG < 5, "0 problem", "1-4 problem"),
         drug = ifelse(DRUG_CUTDOWN + DRUG_ANNOYED + DRUG_GUILTY + 
                         DRUG_DRUG < 5, "0 problem", "1-4 problem")) |> 
  select(-MARITAL, -starts_with("JOB"), -ADULT, -CHILDREN, -AMBULATORY, -SMOKING,
         -starts_with("ALCOHOL", FALSE), -starts_with("DRUG", FALSE))
```








```{r}
survey$DEMO_HIS_HISTORY_GRID %<>% select(USUBJID, DEMO_HIS_HISTORY_GRID_SEQ,
                                         HIS_CONDITION, HIS_YN)

survey$DIS %<>% select(USUBJID, FINAL_DIAG_ICD10)
survey$ANT %<>% select(USUBJID, ANB_HOS)
survey$ANT_ANB_HOSP_GRID %<>% select(USUBJID, ANB_OTHER_SPEC)
```



## Admission dataset

```{r Admission variables}
survey$ADM <- survey$ADM %>%
  mutate(hospitaltype = ifelse(SITEID %in% c("010","159"), 1, 2),
         age = 2025 - YEAR_BIRTH + 1,
         Ab_history = ifelse(ANB_ADMISSION %in% c(1, 4), 0, 1),
         wardtype = as.factor(ifelse(WARD_3 == 1, "surgical", "medical/ID")))

admission <- discharge_date |>
  merge2(survey$SCR) |>
  mutate(DISCHARGE_DATE = ifelse(is.na(SPEC_DATE_DISCHARGE),
                                 `Discharge date`, SPEC_DATE_DISCHARGE)) %>%
  select(USUBJID, DISCHARGE_DATE) |> 
  merge2(survey$ADM) %>%
  mutate(los = as.numeric((as.POSIXct(DISCHARGE_DATE) -
                             as.POSIXct(ADMISSION_DATE)) / 86400 + 1))
```


## General info dataset

```{r}
unique(survey$DEMO_HIS$JOB_final)
```


```{r General information}
survey$DEMO_HIS <- survey$DEMO_HIS %>%
  mutate(JOB_final = case_match(JOB_SPECIFY,
                                c("Cán bộ công chức", "Cán bộ xã") ~ 1,
                                c("Bảo vệ", "Cơ khí","Hộ lý", "Lái tàu thủy",
                                  "Lao động tự do", "Vệ sỹ") ~ 4,
                                c("già", "Già", "Hết độ tuổi lao động") ~ 8,
                                c("Ở nhà", "Tự do") ~ 9, .default = as.numeric(JOB)),
         householdsize = ADULT + CHILDREN,
         ALCOHOL_CUTDOWN_score = ALCOHOL_CUTDOWN != 1,
         ALCOHOL_ANNOYED_score = ALCOHOL_ANNOYED != 1,
         ALCOHOL_GUILTY_score = ALCOHOL_GUILTY != 1,
         ALCOHOL_DRUG_score = ALCOHOL_DRUG != 1,
         DRUG_CUTDOWN_score = DRUG_CUTDOWN != 1,
         DRUG_ANNOYED_score = DRUG_ANNOYED != 1,
         DRUG_GUILTY_score = DRUG_GUILTY != 1,
         DRUG_DRUG_score = DRUG_DRUG != 1,
         smoking = as.factor(case_match(SMOKING,
                                        "1" ~ "current smoker",
                                        "2" ~ "former smoker",
                                        .default = "all non-smokers")),
         children = as.factor(ifelse(CHILDREN == 0,
                                     "no children in the household",
                                     "with children in the household")),
         married = as.factor(ifelse(MARITAL == 1, "married", "other")),
         ambulatory = as.factor(ifelse(AMBULATORY == 1,
                                       "independent", "not independent")),
         AlcoholCAGE = ALCOHOL_CUTDOWN_score + ALCOHOL_ANNOYED_score +
           ALCOHOL_GUILTY_score + ALCOHOL_DRUG_score, 
         DrugCAGE = DRUG_CUTDOWN_score + DRUG_ANNOYED_score + DRUG_GUILTY_score +
           DRUG_DRUG_score,
         job = case_match(JOB_final, 6 ~ "farmer", 7 ~ "housewife", 8 ~ "retired",
                          .default = "all other jobs"),
         alcohol = as.factor(ifelse(AlcoholCAGE == 0, "0 problem", "1-4 problem")),
         drug = as.factor(ifelse(DrugCAGE == 0, "0 problem", "1-4 problem")))
```


## Other history dataset

```{r other history}
## MARC: this is not a good idea

InvasiveHistory <- survey$DEMO_HIS_HISTORY_GRID %>%
  filter(HIS_CONDITION == 1) %>%
  mutate(InvasiveHistory = as.factor(ifelse(HIS_YN == 2, "Yes", "No")))
         
MedicationHistory <- survey$DEMO_HIS_HISTORY_GRID %>%
  filter(HIS_CONDITION == 2) %>%
  mutate(MedicationHistory = as.factor(ifelse(HIS_YN == 2, "Yes", "No")))

TravelHistory <- survey$DEMO_HIS_HISTORY_GRID %>%
  filter(HIS_CONDITION == 3) %>%
  mutate(TravelHistory = as.factor(ifelse(HIS_YN == 2, "Yes", "No")))

HealthcareHistory <- survey$DEMO_HIS_HISTORY_GRID %>%
  filter(HIS_CONDITION == 4) %>%
  mutate(HealthcareHistory = as.factor(ifelse(HIS_YN == 2, "Yes", "No")))
```


## Discharge dataset

The categories:

```{r}
id_intestinal <- c("A04", "A04.8", "A04.9", "A05.9", "A06.4", "A08.0", "A08.5", "A09",
                   "A09.0", "A09.9")
id_other <- c("A15.0", "A15.3", "A16.2", "A41", "A41.5", "A41.8", "A41.9", "A48",
              "A49.9", "A79.8", "A79.9", "A93", "A94", "A97", "B00.1", "B01", "B01.2",
              "B01.8", "B02", "B02.7", "B02.8", "B05", "B05.2", "B05.8", "B05.9",
              "B17", "B18.1", "B18.2", "B34.9", "B83.8")
neoplasms <- c("C18", "C18.9; K56.6", "C20", "C22", "C22.9", "C34.9", "C41", "C61",
               "C67.9", "C70.0", "C91.9", "C92.2", "C95.0", "D12.0", "D17", "D21",
               "D21.9", "D23", "D23.9", "D27", "D37.4", "D38.1", "D40.0", "D44.0",
               "D48.1")
circulatory_diseases <- c("I10", "I10-E11-E25-I69", "I10; H81", "I11.9", "I12.5", "I18",
                          "I20", "I20.0", "I20.8", "I21", "I21.4", "I21.9", "I24.0",
                          "I25", "I25.2", "I25.5", "I48", "I48.0", "I48.2", "I50",
                          "I50.9", "I61", "I63", "I63.8", "I64", "I67", "I67-I10",
                          "I67 - I10", "I69.4", "I70.2", "I80", "I87.2", "I88.8",
                          "I92.9", "I95", "I99")
respiratory_diseases <- c("J01", "J01.9", "J02", "J02.9", "J04.0", "J06", "J06.9",
                          "J09", "J10.1", "J10.8", "J11", "J11.1", "J11.8", "J15",
                          "J15.9", "J16", "J17.1", "J18", "J18-I20.2", "J18.0",
                          "J18.1", "J18.8", "J18.9", "J20", "J20.9", "J40", "J42",
                          "J44", "J44.0", "J44.1", "J44.9", "J45", "J90", "J96.0",
                          "J96.9", "J96/18")
digestive_diseases <- c("K11.2", "K12.3", "K21", "K21.0", "K21.9", "K22.6", "K25",
                        "K25.0", "K25.3", "K25.9", "K26.0", "K27", "K27-J20", "K27.0",
                        "K27.3", "K27.9", "K29", "K29.0", "K29.1", "K29.2", "K29.6",
                        "K29.9", "K30", "K35", "K35.1", "K35.3", "K35.5", "K35.8",
                        "K35.9", "K36", "K40", "K40.9", "K42", "K50", "K52.3", "K52.9",
                        "K56", "K56.4", "K56.6", "K57.0", "K57.3", "K57.9", "K58",
                        "K58.0", "K59.1", "K60.3", "K61.0", "K61.2", "K62.1", "K62.5",
                        "K63", "K63.1", "K63.5", "K64", "K64.2", "K64.3", "K64.8",
                        "K65", "K71.2", "K71.6", "K72.0", "K72.2", "K73", "K74",
                        "K74.0", "K74.1", "K74.2", "K74.6", "K75.8", "K77", "K78.6",
                        "K80", "K80.0", "K80.1", "K80.2", "K80.3", "K80.4", "K80.8",
                        "K81", "K81.0", "K83", "K83.0", "K85", "K85.0", "K85.8",
                        "K85.9", "K86.1", "K92", "K92.2", "K92.8", "K92.9")
genitourinary_diseases <- c("N00", "N13.2", "N13.3", "N13.6", "N17", "N17.9", "N18",
                            "N18.4", "N18.5", "N18.9", "N19", "N20", "N20.0", "N20.1",
                            "N20.1, N23, N20.0, K21, M47", "N20.2", "N21.0", "N21.1",
                            "N23", "N28", "N30.0", "N30.8", "N32.0", "N34.1", "N39.0",
                            "N40", "N43.2", "N45", "N47", "N48.1", "N70")
```

Tests:

```{r}
unique_codes <- unique(survey$DIS$FINAL_DIAG_ICD10)
all_codes <- c(id_intestinal, id_other, neoplasms, circulatory_diseases,
               respiratory_diseases, digestive_diseases, genitourinary_diseases)

all_codes |> 
  table() |> 
  unique()

all(all_codes %in% unique_codes)
setdiff(all_codes, unique_codes)
```


```{r discharge dataset}
discharge <- survey$DIS %>%
  mutate(ICDGroup = as.factor(case_when(
           FINAL_DIAG_ICD10 %in% id_intestinal ~ "ID (Intestinal)",
           FINAL_DIAG_ICD10 %in% id_other ~ "ID (Other)",
           FINAL_DIAG_ICD10 %in% neoplasms ~ "Neoplasms",
           FINAL_DIAG_ICD10 %in% circulatory_diseases ~ "Circulatory diseases",
           FINAL_DIAG_ICD10 %in% respiratory_diseases ~ "Respiratory diseases",
           FINAL_DIAG_ICD10 %in% digestive_diseases ~ "Digestive diseases",
           FINAL_DIAG_ICD10 %in% genitourinary_diseases ~ "Genitourinary diseases",
           .default = "Other")),
         ICUduration = difftime(ICU_TO, ICU_FROM, units = "days") + 1,
         CVCduration = difftime(CVC_TO, CVC_FROM, units = "days") + 1,
         PVCduration = difftime(PVC_TO, PVC_FROM, units = "days") + 1,
         UCduration = difftime(UC_TO, UC_FROM, units = "days") + 1,
         IIDduration = difftime(IID_TO, IID_FROM, units = "days") + 1)
```

## Antibiotic use during hospitalization

```{r}
cefoperazone <- c("Cefoperazol","Cefoperazole", "Cefoperazon", "Cefoperazone")
ampicill_sulb <- "Senitram"
cefamandol <- c("Cefamandol", "Cefemandol")
cefo_sulb <- "Vitabactam"
cefazolin <- "Cefazolin"
cefprozil <- "Cefprozil"
cefradin <- "Cefradin"
ceftizoxime <- c("Ceftizoxim", "Ceftizoxime", "Ceftizoxom", "Ceftrizoxim")
cefmetazol <- "Cefmetazol"
ticarcillin_acid_clavulanic <- c("Ticarcillin + Acid clavulanic",
                                 "Ticarcillin + Clavulanic",
                                 "Ticarcillin/acid clavulanic")
```

Tests:

```{r}
unique_ab <- unique(survey$ANT_ANB_HOSP_GRID$ANB_OTHER_SPEC)
all_ab <- c(cefoperazone, ampicill_sulb, cefamandol, cefo_sulb,
            cefazolin, cefprozil, cefradin, ceftizoxime, cefmetazol,
            ticarcillin_acid_clavulanic)

all_ab |> 
  table() |> 
  unique()

all(all_ab %in% unique_ab)
setdiff(all_ab, unique_ab)
```

```{r ANTIBIOTIC USE DURING HOSPITALIZATION}
# Antibiotic use during hospitalization at patient level
antibiotic_hospital <- survey$ANT %>%
  mutate(antibiotic_hospital = ifelse(ANB_HOS == 3, "yes", "no"))

#antibiotic agents used in hospital, each patient can have more than 1 antibiotic agent
antibiotic_hospital_agents <- survey$ANT_ANB_HOSP_GRID %>%
  mutate(agent = case_when(ANB_OTHER_SPEC %in% cefoperazone ~ "Cefoperazone",
                           ANB_OTHER_SPEC %in% ampicill_sulb ~ "Ampicillin_sulbactam",
                           ANB_OTHER_SPEC %in% cefamandol ~ "Cefamandol",
                           ANB_OTHER_SPEC %in% cefo_sulb ~ "Cefoperazone_sulbactam",
                           ANB_OTHER_SPEC %in% cefazolin ~ "Cefazolin",
                           ANB_OTHER_SPEC %in% cefprozil ~ "Cefprozil",
                           ANB_OTHER_SPEC %in% cefradin ~ "Cefradin",
                           ANB_OTHER_SPEC %in% ceftizoxime ~ "Ceftizoxime",
                           ANB_OTHER_SPEC %in% cefmetazol ~ "Cefmetazol",
                           ANB_OTHER_SPEC %in% ticarcillin_acid_clavulanic ~
                             "Ticarcillin/acid clavulanic",
                           .default = ANB_HOSP_NAME),
         number = 1,
         DOT = as.numeric((ANB_HOSP_END_DATE - ANB_HOSP_START_DATE) / 86400 + 1))

# calculate DOT of antibiotics used in hospital for each patient, at patient level
antibiotic_hospital_DOT <- antibiotic_hospital_agents %>%
  group_by(USUBJID) %>%
  summarise(number = sum(number), DOT = sum(DOT))
```


## merge all data in the CRF

``` {r merge CRF datasets}
#select the variables that are relevant for further modeling
all_data <- list(
    admission,
    select(survey$DEMO_HIS, USUBJID, smoking, children, married, ambulatory, job,
           alcohol, drug),
    select(InvasiveHistory, USUBJID, InvasiveHistory),
    select(MedicationHistory, USUBJID, MedicationHistory),
    select(TravelHistory, USUBJID, TravelHistory),
    select(HealthcareHistory, USUBJID, HealthcareHistory),
    select(discharge, USUBJID, ICDGroup, ICUduration, CVCduration, PVCduration,
           UCduration, IIDduration, DISCHARGE, ICU, CVC, PVC, UC, IID),
    select(antibiotic_hospital, USUBJID, antibiotic_hospital),
    antibiotic_hospital_DOT) |> 
  reduce(merge2)

# to add CRE data depending on type of carriage examined for further analysis
```


# Prepare risk datasets for Lasso modeling

```{r risk datasets}
riskdata <- merge2(all_data, CREC_admission) %>%
  mutate(CRE_carriage = ! is.na(SPEC_DATE),
         smoking2 = as.factor(ifelse(smoking == "all non-smokers",
                                     "all non-smokers", "smokers")),
         children2 = as.factor(ifelse(is.na(children), 1, children)), 
# NA to be classified as 1 = having no children living in the house; 2 = having children living in the house
         job_farmer = as.factor(ifelse(job == "farmer", "farmers", "allothers")),# 1 = others, 3 = housewife, 4 = retired, 2 = farmers
         job_housewife = as.factor(ifelse(job == "housewife", "housewives", "allothers")), # 1 = others, 3 = housewife, 4 = retired, 2 = farmers
         job_retired = as.factor(ifelse(job == "retired", "retired", "allothers")), # 1 = others, 3 = housewife, 4 = retired, 2 = farmers
         heart_diseases = as.factor(ifelse(as.factor(MI_HIS + CHF) == 0, 0, 1)),
         vascular_diseases = as.factor(ifelse(as.factor(CVD + PVD) == 0, 0, 1)),
         cancer = as.factor(TUMOR_NOMETA + LEUKEMIA + LYMPHOMA + META_TUMOR),
         values = TRUE) |> 
  pivot_wider(names_from = ICDGroup, values_from = values, values_fill = FALSE)
```



# Prepare variables for Lasso modeling

```{r scaling and fixing data for Lasso}
# standardize predictor variables before Lasso regression because the penalty is
# applied to the magnitude of coefficients; standardizing (to mean 0, std dev 1)
# ensures all variables are treated equally, allowing for meaningful coefficient
# comparison and selection based on true predictive power, not scale. Check Defaults:
# Confirm glmmLassoControl settings; standardize = TRUE is the standard for 2026 to
# ensure the L1 penalty is consistent. Factor Recognition: Ensure categorical variables
# are recognized as factors so the algorithm can apply group-wise updates. 

#for continuous variables - check if re-scaled back when interpreting

riskdata_scaled <- riskdata %>% 
  mutate(age_s = scale(age), 
         across(c(GENDER, SITEID, CORMOBIDITY, DEMENTIA, CPD, CTD, PUD, MILD_LIVER,
                  SEV_LIVER, HEMIPLEGIA, SEV_RENAL, DIAB_NOEOD, DIAB_EOD),
                as.factor)) |> 
  select(CRE_carriage, age_s, GENDER, smoking2, SITEID, children2, married, ambulatory,
         job_farmer, job_housewife, job_retired, CORMOBIDITY, heart_diseases,
         vascular_diseases, DEMENTIA, CPD, CTD, PUD, MILD_LIVER, SEV_LIVER, HEMIPLEGIA,
         SEV_RENAL, DIAB_NOEOD, DIAB_EOD, cancer, alcohol, drug, wardtype, Ab_history,
         InvasiveHistory, MedicationHistory, HealthcareHistory, hospitaltype,
         `Circulatory diseases`, `Genitourinary diseases`, `ID (Intestinal)`,
         `ID (Other)`, Neoplasms, `Respiratory diseases`, `Digestive diseases`)
#         gender = as.factor(GENDER),
#         hospital = as.factor(SITEID),
#         cormobidity = as.factor(CORMOBIDITY),
#         dementia = as.factor(DEMENTIA),
#         cpd = as.factor(CPD),
#         ctd = as.factor(CTD),
#         pud = as.factor(PUD),
#         mild_liver = as.factor(MILD_LIVER),
#         sev_liver = as.factor(SEV_LIVER),
#         hemiplegia = as.factor(HEMIPLEGIA),
#         sev_renal = as.factor(SEV_RENAL),
#         diabetes_noeod = as.factor(DIAB_NOEOD),
#         diabetes_eod = as.factor(DIAB_EOD),

#no patient has AIDS, also not include pvd as no cases have pvd

data_clean <- na.exclude(riskdata_scaled)
nrow(riskdata_scaled) - nrow(data_clean) # Check how many rows you lost
```

# Fit a simple glmm model

```{r fit a simple model glmm}
mixed_formula <- CRE_carriage ~ age_s + GENDER + smoking2 + children2 + married +
  ambulatory + job_farmer + job_housewife + job_retired + CORMOBIDITY + 
  vascular_diseases + CPD + CTD + PUD + MILD_LIVER + SEV_LIVER + HEMIPLEGIA +
  SEV_RENAL + DIAB_NOEOD + DIAB_EOD + cancer + alcohol + drug + wardtype +
  InvasiveHistory + MedicationHistory + HealthcareHistory + hospitaltype + Ab_history +
  `Circulatory diseases` + `Genitourinary diseases` + `ID (Intestinal)` +
  `ID (Other)` + Neoplasms + `Respiratory diseases` + `Digestive diseases` +
  (1| SITEID)                           # not include heart_diseases and dementia yet -


simple_mixed_model <- glmer(mixed_formula, data_clean, binomial(link = "logit"))
summary(simple_mixed_model)
initial_fixed_estimates <- fixef(simple_mixed_model)
initial_random_estimates <- ranef(simple_mixed_model)
Delta.start <- c(as.numeric(initial_fixed_estimates), rep(0, 100),
                 as.numeric(initial_random_estimates))
Q.start <- as.numeric(VarCorr(simple_mixed_model))
```

# Find the best lambda for glmmLasso

```{r find best lambda for glmmLasso}
# Define a sequence of lambda values (from high penalty to low)
lambda_seq <- seq(10, 0, by = -.1)

#fixed formula
fixed_formula <- update(mixed_formula, . ~ . - (1| SITEID))

# Initialize a vector to store BIC or AIC values
baic_vec <- rep(Inf, length(lambda_seq))

# Create a loop to test each lambda
for(j in 1:length(lambda_seq)) {
  print(paste("Testing Lambda:", lambda_seq[j]))
  #Use try() to prevent the loop from breaking if one model fails to converge
  glmm_temp <- try(glmmLasso(
    fix = fixed_formula,
    rnd = list(hospital = ~1),
    data = data_clean,
    lambda = lambda_seq[j],
    family = binomial(),
    switch.NR = TRUE,
    final.re = FALSE,
    control = list(start = Delta.start, q_start = Q.start)),
    silent = TRUE)
  #If the model fit successfully, save the BIC
  if (!inherits(glmm_temp, "try-error")) baic_vec[j] <- glmm_temp$bic
}

# Find the lambda that produced the lowest BIC
(opt_lambda <- lambda_seq[which.min(baic_vec)])
baic_vec
lambda_seq[which(is.infinite(baic_vec))]
```

# Fit the final Lasso model

```{r fit model}
CRE_admission_model <- glmmLasso(
  fix = fixed_formula,
  rnd = list(hospital = ~1),
  data = data_clean,
  lambda = opt_lambda, # larger -> stronger regularization and more coefficients shrunk to zero; smaller reduces penalty
  family = binomial(link = logit),
  switch.NR = FALSE, # switch to the faster Newton-Raphson method to speed up model fitting process
  final.re = TRUE,
  control = list(start = Delta.start, q_start = Q.start))

(model_summary <- summary(CRE_admission_model))
```

# Final estimates

``` {r extract ORs and 95%CI}
std_errors <- model_summary$coefficients[, "StdErr"]; 
tab <- cbind(Est = coef(CRE_admission_model),
             LL = coef(CRE_admission_model) - 1.96 * std_errors,
             UL = coef(CRE_admission_model) + 1.96 * std_errors); 
round(cbind(exp(tab), p = coef(summary(CRE_admission_model))[, 4]), digits = 3) #p-value
```
                                 