---
title: "60HN - ASPARNet study - CRE Admission Risk: Datasets, Variables and Models"
author: "Vu Thi Lan Huong"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_depth: 2
    number_sections: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document: default
editor_options: 
  chunk_output_type: console
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Packages

```{r packages}
library(dplyr)
library(stringr)
library(readxl)
library(gmodels)
library(lsmeans)
library(dplyr)
library(lme4)
library(glmmLasso)
```


# Constants

```{r constants}
if (grepl("arc|hoisy", Sys.getenv("USER"))) {
  path2data <- paste0("~/Library/CloudStorage/OneDrive-OxfordUniversityClinical",
                      "ResearchUnit/GitHub/HuongVTL/CRE-gut-acquisition/")
} else {
  path2data <- paste("C:/Users/huongvtl/OneDrive - Oxford University Clinical",
                     "Research Unit/60HN CRE transmission manuscript/")
}
```


# Functions

```{r}
"%ni%" <- Negate("%in%")
```

```{r}
make_path <- function(file) paste0(path2data, file)
```

Tuning `read_excel()`:

```{r}
read_excel2 <- function(file, ...) read_excel(make_path(file), ...)
```

Tuning `excel_sheets()`:

```{r}
excel_sheets2 <- function(file) excel_sheets(make_path(file))
```

A function that reads all the sheets of an excel file:

``` {r}
readxl_allsheet <- function(filename, tibble = FALSE) {
  # I prefer straight data.frames
  # but if you like tidyverse tibbles (the default with read_excel)
  # then just pass tibble = TRUE
  sheets <- filename |>
    excel_sheets2() |> 
    setdiff("Category")
  x <- lapply(sheets, function(X) {
    filename |>
      read_excel2(sheet = X) |> 
      filter(entry == 2)
  })
  if(!tibble) x <- lapply(x, as.data.frame)
  names(x) <- sheets
  x
}
```


# Datasets and variables

## Source data

The list of non-CRE bacteria to exclude from the data:

```{r}
non_CRE <- c("Acinetobacter baumannii", "Aeromonas caviae", "Aeromonas hydrophila",
             "Aeromonas veronii", "Enterococcus faecium", "Cupriavidus gilardii",
             "Pseudomonas putida")
```

Reading the data sets:

```{r load data}
survey <- readxl_allsheet("16-12-2025-_60HN_PATIENT_P1_Data.xls")
cre <- read_excel2("60HN_ID_MALDITOF_confirmation_20251128.xlsx") |> 
  filter(Identification_MALDITOF %ni% non_CRE) |> 
  mutate(hospitaltype = ifelse(SiteID %in% c("010","159"), 1, 2))
discharge_date <- read_excel2("60HN - DischargeDate_no_discharge_sample_27Nov25.xlsx")
```


## CRE datasets

```{r}
remove_duplicates <- function(x) {
  x |>
    select(USUBJID, SPEC_DATE) |> 
    unique()
}
```

```{r cre carriage and species}
CRE_admission <- subset(cre, cre$SampleSchedule == "ADMISSION"); 
CRE_discharge <- subset(cre, cre$SampleSchedule == "DISCHARGE")

length(unique(CRE_admission$USUBJID))
length(unique(CRE_discharge$USUBJID))

## subset to specific CREC or CRKP
CREC_admission <- CRE_admission %>%
  filter(Identification_MALDITOF == "Escherichia coli") %>%
  remove_duplicates()

CREC_discharge <- CRE_discharge %>%
  filter(Identification_MALDITOF == "Escherichia coli") %>%
  remove_duplicates()

CRKP_admission <- CRE_admission %>%
  filter(Identification_MALDITOF == "Klebsiella pneumoniae") %>%
  remove_duplicates()

CRKP_discharge <- CRE_discharge %>%
  filter(Identification_MALDITOF == "Klebsiella pneumoniae") %>%
  remove_duplicates()
```


## Admission dataset

```{r Admission variables}
survey[["ADM"]] <- survey[["ADM"]] %>%
  mutate(hospitaltype = ifelse(SITEID %in% c("010","159"), 1, 2),
         age = 2025 - YEAR_BIRTH + 1,
         Ab_history = ifelse(ANB_ADMISSION %in% c(1, 4), 0, 1),
         wardtype = as.factor(ifelse(WARD_3 == 1, "surgical", "medical/ID")))

admission <- discharge_date |>
  merge(survey[["SCR"]], by = "USUBJID", all = TRUE) |>
  mutate(DISCHARGE_DATE = ifelse(is.na(SPEC_DATE_DISCHARGE),
                                 `Discharge date`, SPEC_DATE_DISCHARGE)) %>%
  select(USUBJID, DISCHARGE_DATE) |> 
  merge(survey[["ADM"]], by = "USUBJID", all = TRUE) %>%
  mutate(los = as.numeric((as.POSIXct(DISCHARGE_DATE) -
                             as.POSIXct(ADMISSION_DATE)) / 86400 + 1))
```


## General info dataset

```{r}
unique(survey[["DEMO_HIS"]]$JOB_final)
```


```{r General information}
survey[["DEMO_HIS"]] <- survey[["DEMO_HIS"]] %>%
  mutate(JOB_final = case_match(JOB_SPECIFY,
                                c("Cán bộ công chức", "Cán bộ xã") ~ 1,
                                c("Bảo vệ", "Cơ khí","Hộ lý", "Lái tàu thủy",
                                  "Lao động tự do", "Vệ sỹ") ~ 4,
                                c("già", "Già", "Hết độ tuổi lao động") ~ 8,
                                c("Ở nhà", "Tự do") ~ 9, .default = as.numeric(JOB)),
         householdsize = ADULT + CHILDREN,
         ALCOHOL_CUTDOWN_score = ALCOHOL_CUTDOWN != 1,
         ALCOHOL_ANNOYED_score = ALCOHOL_ANNOYED != 1,
         ALCOHOL_GUILTY_score = ALCOHOL_GUILTY != 1,
         ALCOHOL_DRUG_score = ALCOHOL_DRUG != 1,
         DRUG_CUTDOWN_score = DRUG_CUTDOWN != 1,
         DRUG_ANNOYED_score = DRUG_ANNOYED != 1,
         DRUG_GUILTY_score = DRUG_GUILTY != 1,
         DRUG_DRUG_score = DRUG_DRUG != 1,
         smoking = as.factor(case_match(SMOKING,
                                        "1" ~ "current smoker",
                                        "2" ~ "former smoker",
                                        .default = "all non-smokers")),
         children = as.factor(ifelse(CHILDREN == 0,
                                     "no children in the household",
                                     "with children in the household")),
         married = as.factor(ifelse(MARITAL == 1, "married", "other")),
         ambulatory = as.factor(ifelse(AMBULATORY == 1,
                                       "independent", "not independent")),
         AlcoholCAGE = ALCOHOL_CUTDOWN_score + ALCOHOL_ANNOYED_score +
           ALCOHOL_GUILTY_score + ALCOHOL_DRUG_score, 
         DrugCAGE = DRUG_CUTDOWN_score + DRUG_ANNOYED_score + DRUG_GUILTY_score +
           DRUG_DRUG_score,
         job = case_match(JOB_final, 6 ~ "farmer", 7 ~ "housewife", 8 ~ "retired",
                          .default = "all other jobs"),
         alcohol = as.factor(ifelse(AlcoholCAGE == 0, "0 problem", "1-4 problem")),
         drug = as.factor(ifelse(DrugCAGE == 0, "0 problem", "1-4 problem")))
```


## Other history dataset

```{r other history}
## MARC: this is not a good idea

InvasiveHistory <- survey[["DEMO_HIS_HISTORY_GRID"]] %>%
  filter(HIS_CONDITION == 1) %>%
  mutate(InvasiveHistory = as.factor(ifelse(HIS_YN == 2, "Yes", "No")))
         
MedicationHistory <- survey[["DEMO_HIS_HISTORY_GRID"]] %>%
  filter(HIS_CONDITION == 2) %>%
  mutate(MedicationHistory = as.factor(ifelse(HIS_YN == 2, "Yes", "No")))

TravelHistory <- survey[["DEMO_HIS_HISTORY_GRID"]] %>%
  filter(HIS_CONDITION == 3) %>%
  mutate(TravelHistory = as.factor(ifelse(HIS_YN == 2, "Yes", "No")))

HealthcareHistory <- survey[["DEMO_HIS_HISTORY_GRID"]] %>%
  filter(HIS_CONDITION == 4) %>%
  mutate(HealthcareHistory = as.factor(ifelse(HIS_YN == 2, "Yes", "No")))
```


## Discharge dataset

The categories:

```{r}
id_intestinal <- c("A04", "A04.8", "A04.9", "A05.9", "A06.4", "A08.0", "A08.5", "A09",
                   "A09.0", "A09.9")
id_other <- c("A15.0", "A15.3", "A16.2", "A41", "A41.5", "A41.8", "A41.9", "A48",
              "A49.9", "A79.8", "A79.9", "A93", "A94", "A97", "B00.1", "B01", "B01.2",
              "B01.8", "B02", "B02.7", "B02.8", "B05", "B05.2", "B05.8", "B05.9",
              "B17", "B18.1", "B18.2", "B34.9", "B83.8")
neoplasms <- c("C18", "C18.9; K56.6", "C20", "C22", "C22.9", "C34.9", "C41", "C61",
               "C67.9", "C70.0", "C91.9", "C92.2", "C95.0", "D12.0", "D17", "D21",
               "D21.9", "D23", "D23.9", "D27", "D37.4", "D38.1", "D40.0", "D44.0",
               "D48.1")
circulatory_diseases <- c("I10", "I10-E11-E25-I69", "I10; H81", "I11.9", "I12.5", "I18",
                          "I20", "I20.0", "I20.8", "I21", "I21.4", "I21.9", "I24.0",
                          "I25", "I25.2", "I25.5", "I48", "I48.0", "I48.2", "I50",
                          "I50.9", "I61", "I63", "I63.8", "I64", "I67", "I67-I10",
                          "I67 - I10", "I69.4", "I70.2", "I80", "I87.2", "I88.8",
                          "I92.9", "I95", "I99")
respiratory_diseases <- c("J01", "J01.9", "J02", "J02.9", "J04.0", "J06", "J06.9",
                          "J09", "J10.1", "J10.8", "J11", "J11.1", "J11.8", "J15",
                          "J15.9", "J16", "J17.1", "J18", "J18-I20.2", "J18.0",
                          "J18.1", "J18.8", "J18.9", "J20", "J20.9", "J40", "J42",
                          "J44", "J44.0", "J44.1", "J44.9", "J45", "J90", "J96.0",
                          "J96.9", "J96/18")
digestive_diseases <- c("K11.2", "K12.3", "K21", "K21.0", "K21.9", "K22.6", "K25",
                        "K25.0", "K25.3", "K25.9", "K26.0", "K27", "K27-J20", "K27.0",
                        "K27.3", "K27.9", "K29", "K29.0", "K29.1", "K29.2", "K29.6",
                        "K29.9", "K30", "K35", "K35.1", "K35.3", "K35.5", "K35.8",
                        "K35.9", "K36", "K40", "K40.9", "K42", "K50", "K52.3", "K52.9",
                        "K56", "K56.4", "K56.6", "K57.0", "K57.3", "K57.9", "K58",
                        "K58.0", "K59.1", "K60.3", "K61.0", "K61.2", "K62.1", "K62.5",
                        "K63", "K63.1", "K63.5", "K64", "K64.2", "K64.3", "K64.8",
                        "K65", "K71.2", "K71.6", "K72.0", "K72.2", "K73", "K74",
                        "K74.0", "K74.1", "K74.2", "K74.6", "K75.8", "K77", "K78.6",
                        "K80", "K80.0", "K80.1", "K80.2", "K80.3", "K80.4", "K80.8",
                        "K81", "K81.0", "K83", "K83.0", "K85", "K85.0", "K85.8",
                        "K85.9", "K86.1", "K92", "K92.2", "K92.8", "K92.9")
genitourinary_diseases <- c("N00", "N13.2", "N13.3", "N13.6", "N17", "N17.9", "N18",
                            "N18.4", "N18.5", "N18.9", "N19", "N20", "N20.0", "N20.1",
                            "N20.1, N23, N20.0, K21, M47", "N20.2", "N21.0", "N21.1",
                            "N23", "N28", "N30.0", "N30.8", "N32.0", "N34.1", "N39.0",
                            "N40", "N43.2", "N45", "N47", "N48.1", "N70")
```

Tests:

```{r}
all_codes <- c(id_intestinal, id_other, neoplasms, circulatory_diseases,
               respiratory_diseases, digestive_diseases, genitourinary_diseases)

all_codes |> 
  table() |> 
  unique()

all(all_codes %in% unique(survey[["DIS"]]$FINAL_DIAG_ICD10))
```


```{r discharge dataset}
discharge <- survey[["DIS"]] %>%
  mutate(ICDGroup = as.factor(case_when(
           FINAL_DIAG_ICD10 %in% id_intestinal ~ "ID (Intestinal)",
           FINAL_DIAG_ICD10 %in% id_other ~ "ID (Other)",
           FINAL_DIAG_ICD10 %in% neoplasms ~ "Neoplasms",
           FINAL_DIAG_ICD10 %in% circulatory_diseases ~ "Circulatory diseases",
           FINAL_DIAG_ICD10 %in% respiratory_diseases ~ "Respiratory diseases",
           FINAL_DIAG_ICD10 %in% digestive_diseases ~ "Digestive diseases",
           FINAL_DIAG_ICD10 %in% genitourinary_diseases ~ "Genitourinary diseases",
           TRUE ~ "Other")),
         ICUduration = difftime(ICU_TO, ICU_FROM, units = "days") + 1,
         CVCduration = difftime(CVC_TO, CVC_FROM, units = "days") + 1,
         PVCduration = difftime(PVC_TO, PVC_FROM, units = "days") + 1,
         UCduration = difftime(UC_TO, UC_FROM, units = "days") + 1,
         IIDduration = difftime(IID_TO, IID_FROM, units = "days") + 1)
```

## Antibiotic use during hospitalization

```{r ANTIBIOTIC USE DURING HOSPITALIZATION}
# Antibiotic use during hospitalization at patient level
antibiotic_hospital <- survey[["ANT"]] %>%
  mutate(antibiotic_hospital = ifelse(ANB_HOS == 3, "yes", "no"))

#antibiotic agents used in hospital, each patient can have more than one antibiotic agents
antibiotic_hospital_agents <- survey[["ANT_ANB_HOSP_GRID"]] %>%
  mutate(agent = ifelse(ANB_OTHER_SPEC %in% c("Cefoperazol","Cefoperazole", "Cefoperazon", "Cefoperazone"), "Cefoperazone",
                        ifelse(ANB_OTHER_SPEC %in% c("Senitram"), "Ampicillin_sulbactam",
                               ifelse(ANB_OTHER_SPEC %in% c("Cefamandol","Cefemandol"), "Cefamandol",
                                      ifelse(ANB_OTHER_SPEC %in% c("Vitabactam"), "Cefoperazone_sulbactam",
                                             ifelse(ANB_OTHER_SPEC %in% c("Cefazolin"), "Cefazolin",
                                             ifelse(ANB_OTHER_SPEC %in% c("Cefprozil"), "Cefprozil",
                                                    ifelse(ANB_OTHER_SPEC %in% c("Cefradin"), "Cefradin",
                                                           ifelse(ANB_OTHER_SPEC %in% c("Ceftizoxim", "Ceftizoxime", "Ceftizoxom", "Ceftrizoxim"), "Ceftizoxime",
                                                                  ifelse(ANB_OTHER_SPEC %in% c("Cefprozil"), "Cefprozil",
                                                                  ifelse(ANB_OTHER_SPEC %in% c("Cefmetazol"), "Cefmetazol", 
                                                                         ifelse(ANB_OTHER_SPEC %in% c("Ticarcillin + Acid clavulanic", "Ticarcillin + Clavulanic", "Ticarcillin/acid clavulanic"), "Ticarcillin/acid clavulanic",
                                 ANB_HOSP_NAME))))))))))),
         number = 1,
         DOT = as.numeric((ANB_HOSP_END_DATE-ANB_HOSP_START_DATE)/86400 +1))



# calculate DOT of antibiotics used in hospital for each patient, at patient level
antibiotic_hospital_DOT <- antibiotic_hospital_agents %>%
  group_by(USUBJID) %>%
  summarise(number = sum(number), DOT=sum(DOT))

```

## merge all data in the CRF

``` {r merge CRF datasets}
#select the variables that are relevant for further modeling

all_data <- merge(admission, survey[["DEMO_HIS"]][,c("USUBJID","smoking","children","married","ambulatory","job","alcohol","drug")], by = "USUBJID", all=T )
all_data<- merge(all_data, InvasiveHistory[,c("USUBJID","InvasiveHistory")], by = "USUBJID", all=T )
all_data<- merge(all_data, MedicationHistory[,c("USUBJID","MedicationHistory")], by = "USUBJID", all=T )
all_data<- merge(all_data, TravelHistory[,c("USUBJID","TravelHistory")], by = "USUBJID", all=T )
all_data<- merge(all_data, HealthcareHistory[,c("USUBJID","HealthcareHistory")], by = "USUBJID", all=T )
all_data<- merge(all_data, discharge[,c("USUBJID","ICDGroup","ICUduration","CVCduration","PVCduration","UCduration", "IIDduration",
                                        "DISCHARGE","ICU","CVC","PVC","UC","IID")], by = "USUBJID", all=T )
all_data<- merge(all_data, antibiotic_hospital[, c("USUBJID","antibiotic_hospital")], by = "USUBJID", all=T )
all_data<- merge(all_data, antibiotic_hospital_DOT, by = "USUBJID", all=T )


# to add CRE data depending on type of carriage examined for further analysis
```

# Prepare risk datasets for Lasso modeling

```{r risk datasets}

riskdata <- merge(all_data, CREC_admission, by ="USUBJID", all=T )
riskdata <- riskdata %>%
  mutate(CRE_carriage = ifelse(is.na(SPEC_DATE), 0, 1),
         smoking2 = as.factor(ifelse(smoking == "all non-smokers", "all non-smokers", "smokers")),
         children2 = as.factor(ifelse(is.na(children), 1, children)), 
         # NA to be classified as 1= having no children living in the house; 2 = having children living in the house
         job_farmer = as.factor(ifelse(job == "farmer", "farmers", "allothers")), #1=others, 3=housewife 4= retired 2 = farmers
         job_housewife = as.factor(ifelse(job == "housewife", "housewives", "allothers")), #1=others, 3=housewife 4= retired 2 = farmers
         job_retired = as.factor(ifelse(job == "retired", "retired", "allothers")), #1=others, 3=housewife 4= retired 2 = farmers
         heart_diseases = as.factor(ifelse(as.factor(MI_HIS+CHF)==0, 0, 1)),
         vascular_diseases = as.factor(ifelse(as.factor(CVD+PVD)==0, 0,1)),
         cancer = as.factor(TUMOR_NOMETA + LEUKEMIA + LYMPHOMA + META_TUMOR),
         ICD_Circulatory = as.factor(ifelse(ICDGroup == "Circulatory diseases", "Circulatory diseases", "allothers")), 
         ICD_Genitourinary = as.factor(ifelse(ICDGroup == "Genitourinary diseases", "Genitourinary diseases", "allothers")),
         ICD_IDIntestinal = as.factor(ifelse(ICDGroup == "ID (Intestinal)", "ID (Intestinal)", "allothers")),
         ICD_IDOther = as.factor(ifelse(ICDGroup == "ID (Other)", "ID (Other)", "allothers")),
         ICD_Neoplasms = as.factor(ifelse(ICDGroup == "Neoplasms", "Neoplasms", "allothers")),
         ICD_Digestive = as.factor(ifelse(ICDGroup == "Digestive diseases", "Digestive diseases", "allothers")),
         ICD_Respiratory = as.factor(ifelse(ICDGroup == "Respiratory diseases", "Respiratory diseases", "allothers")),
         )

```

# Prepare variables for Lasso modeling

```{r scaling and fixing data for Lasso}
###standardize predictor variables before Lasso regression because the penalty is applied to the magnitude of coefficients; standardizing (to mean 0, std dev 1) ensures all variables are treated equally, allowing for meaningful coefficient comparison and selection based on true predictive power, not scale.
##Check Defaults: Confirm glmmLassoControl settings; standardize = TRUE is the standard for 2026 to ensure the L1 penalty is consistent.
##Factor Recognition: Ensure categorical variables are recognized as factors so the algorithm can apply group-wise updates. 

#for continuous variables - check if re-scaled back when interpreting

riskdata_scaled <- 
  riskdata %>% 
  mutate(
    age_s = scale(age), 
    gender = as.factor(GENDER),
    hospital = as.factor(SITEID),
    cormobidity = as.factor(CORMOBIDITY),
    dementia = as.factor(DEMENTIA),
    cpd = as.factor(CPD),
    ctd = as.factor(CTD),
    pud = as.factor(PUD),
    mild_liver = as.factor(MILD_LIVER),
    sev_liver = as.factor(SEV_LIVER),
    hemiplegia = as.factor(HEMIPLEGIA),
    sev_renal = as.factor(SEV_RENAL),
    diabetes_noeod = as.factor(DIAB_NOEOD),
    diabetes_eod = as.factor(DIAB_EOD),
  )

#no patient has AIDS, also not include pvd as no cases have pvd

## to fix NAs and check data
vars_to_keep <- c("CRE_carriage", "age_s", "gender", "smoking2","hospital", "SITEID", "children2", "married", "ambulatory", "job_farmer", "job_housewife", "job_retired", "cormobidity", "heart_diseases", "vascular_diseases", "dementia", "cpd", "ctd","pud","mild_liver", "sev_liver", "hemiplegia", "sev_renal", "diabetes_noeod","diabetes_eod", "cancer","alcohol", "drug","wardtype","Ab_history", "InvasiveHistory", "MedicationHistory","HealthcareHistory", "hospitaltype", "ICD_Circulatory", "ICD_Genitourinary", "ICD_IDIntestinal", "ICD_IDOther", "ICD_Neoplasms", "ICD_Respiratory", "ICD_Digestive")

data_clean <- riskdata_scaled[complete.cases(riskdata_scaled[,vars_to_keep]),]

print(nrow(riskdata_scaled) - nrow(data_clean)) # Check how many rows you lost
```

# Fit a simple glmm model

```{r fit a simple model glmm}

mixed_formula <- CRE_carriage ~ age_s +gender+smoking2+children2+married+ambulatory+
  job_farmer+job_housewife+job_retired+cormobidity+
  vascular_diseases+cpd+ctd+pud+mild_liver+sev_liver+hemiplegia+sev_renal+diabetes_noeod+diabetes_eod+cancer+
  alcohol +drug+wardtype+InvasiveHistory +MedicationHistory+HealthcareHistory + hospitaltype+ Ab_history+
  ICD_Circulatory + ICD_Genitourinary + ICD_IDIntestinal + ICD_IDOther +
  ICD_Neoplasms+ICD_Respiratory+ICD_Digestive +( 1| SITEID) #not include heart_diseases and dementia yet -


simple_mixed_model <- glmer(mixed_formula, data = data_clean, family = binomial(link = "logit"))
summary(simple_mixed_model)
initial_fixed_estimates <- fixef(simple_mixed_model)
initial_random_estimates <- ranef(simple_mixed_model)
Delta.start<-c(as.numeric(initial_fixed_estimates),rep(0,100),
               as.numeric(initial_random_estimates))
Q.start<-as.numeric(VarCorr(simple_mixed_model))

```

# Find the best lambda for glmmLasso

```{r find best lambda for glmmLasso}

# Define a sequence of lambda values (from high penalty to low)
lambda_seq <- seq(10, 0, by = -0.1)

#fixed formula
fixed_formula <- CRE_carriage ~ age_s +gender+smoking2+children2+married+ambulatory+
  job_farmer+job_housewife+job_retired+cormobidity+
  vascular_diseases+cpd+ctd+pud+mild_liver+sev_liver+hemiplegia+sev_renal+diabetes_noeod+diabetes_eod+cancer+
  alcohol +drug+wardtype+InvasiveHistory +MedicationHistory+HealthcareHistory + hospitaltype+ Ab_history+
  ICD_Circulatory + ICD_Genitourinary + ICD_IDIntestinal + ICD_IDOther +
  ICD_Neoplasms+ICD_Respiratory+ICD_Digestive

# Initialize a vector to store BIC or AIC values
baic_vec <- rep(Inf, length(lambda_seq))

# Create a loop to test each lambda
for(j in 1:length(lambda_seq)){
  print(paste("Testing Lambda:", lambda_seq[j]))
  #Use try() to prevent the loop from breaking if one model fails to converge
  glmm_temp <- try(glmmLasso(
    fix = fixed_formula,
    rnd = list(hospital=~1),
    data = data_clean,
    lambda = lambda_seq[j],
    family = binomial(),
    switch.NR = TRUE,
    final.re = FALSE,
    control=list(start=Delta.start,q_start=Q.start)),
    silent = TRUE)
  #If the model fit successfully, save the BIC
  if(!inherits(glmm_temp, "try-error")){
    baic_vec[j] <- glmm_temp$bic
  }
}

# Find the lambda that produced the lowest BIC
opt_lambda <- lambda_seq[which.min(baic_vec)]
print(paste("Optimal Lambda is:", opt_lambda))

baic_vec

failed_indices <- which(is.infinite(baic_vec))
print(lambda_seq[failed_indices])



```

# Fit the final Lasso model

```{r fit model}

CRE_admission_model <- glmmLasso(
  fix=fixed_formula,
  rnd=list(hospital = ~1),
  data = data_clean,
  lambda = opt_lambda, # larger -> stronger regularization and more coefficients shrunk to zero; smaller reduces penalty
  family = binomial(link = logit),
  switch.NR=FALSE, # switch to the faster Newton-Raphson method to speed up model fitting process
  final.re=TRUE,
  control=list(start=Delta.start,q_start=Q.start)
  )

CRE_admission_model %>% summary()
model_summary <- summary(CRE_admission_model)

```

# Final estimates

``` {r extract ORs and 95%CI}

std_errors <- model_summary$coefficients[, "StdErr"]; 
tab <- cbind(Est = coef(CRE_admission_model), LL = coef(CRE_admission_model) - 1.96 * std_errors, UL = coef(CRE_admission_model) + 1.96 *std_errors); 

round(cbind(exp(tab),p=coef(summary(CRE_admission_model))[,4]),digits = 3) #p-value


```
                                 