---
title: "60HN - ASPARNet study - CRE Admission Risk: Datasets, Variables and Models"
author: "Vu Thi Lan Huong"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_depth: 2
    number_sections: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document: default
editor_options: 
  chunk_output_type: console
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Constants

CRF file:

```{r}
CRF_file <- "16-12-2025-_60HN_PATIENT_P1_Data.xls"
```

MALDI-TOF file:

```{r}
malditof_file <- "60HN_ID_MALDITOF_confirmation_20251128.xlsx"
```

The dates of discharge of the patients who did no provide any sample at discharge:

```{r}
no_sample_discharge_dates <- "60HN - DischargeDate_no_discharge_sample_27Nov25.xlsx"
```

Bacteria to exclude from the analysis:

```{r}
non_CRE <- c("Acinetobacter baumannii", "Aeromonas caviae", "Aeromonas hydrophila",
             "Aeromonas veronii", "Enterococcus faecium", "Cupriavidus gilardii",
             "Pseudomonas putida")
```

The diseases categories:

```{r}
id_intestinal <- c("A04", "A04.8", "A04.9", "A05.9", "A06.4", "A08.0", "A08.5", "A09",
                   "A09.0", "A09.9")
id_other <- c("A15.0", "A15.3", "A16.2", "A41", "A41.5", "A41.8", "A41.9", "A48",
              "A49.9", "A79.8", "A79.9", "A93", "A94", "A97", "B00.1", "B01", "B01.2",
              "B01.8", "B02", "B02.7", "B02.8", "B05", "B05.2", "B05.8", "B05.9",
              "B17", "B18.1", "B18.2", "B34.9", "B83.8")
neoplasms <- c("C18", "C18.9; K56.6", "C20", "C22", "C22.9", "C34.9", "C41", "C61",
               "C67.9", "C70.0", "C91.9", "C92.2", "C95.0", "D12.0", "D17", "D21",
               "D21.9", "D23", "D23.9", "D27", "D37.4", "D38.1", "D40.0", "D44.0",
               "D48.1")
circulatory_diseases <- c("I10", "I10-E11-E25-I69", "I10; H81", "I11.9", "I12.5",
                          "I18", "I20", "I20.0", "I20.8", "I21", "I21.4", "I21.9",
                          "I24.0", "I25", "I25.2", "I25.5", "I48", "I48.0", "I48.2",
                          "I50", "I50.9", "I61", "I63", "I63.8", "I64", "I67",
                          "I67-I10", "I67 - I10", "I69.4", "I70.2", "I80", "I87.2",
                          "I88.8", "I92.9", "I95", "I99")
respiratory_diseases <- c("J01", "J01.9", "J02", "J02.9", "J04.0", "J06", "J06.9",
                          "J09", "J10.1", "J10.8", "J11", "J11.1", "J11.8", "J15",
                          "J15.9", "J16", "J17.1", "J18", "J18-I20.2", "J18.0",
                          "J18.1", "J18.8", "J18.9", "J20", "J20.9", "J40", "J42",
                          "J44", "J44.0", "J44.1", "J44.9", "J45", "J90", "J96.0",
                          "J96.9", "J96/18")
digestive_diseases <- c("K11.2", "K12.3", "K21", "K21.0", "K21.9", "K22.6", "K25",
                        "K25.0", "K25.3", "K25.9", "K26.0", "K27", "K27-J20", "K27.0",
                        "K27.3", "K27.9", "K29", "K29.0", "K29.1", "K29.2", "K29.6",
                        "K29.9", "K30", "K35", "K35.1", "K35.3", "K35.5", "K35.8",
                        "K35.9", "K36", "K40", "K40.9", "K42", "K50", "K52.3", "K52.9",
                        "K56", "K56.4", "K56.6", "K57.0", "K57.3", "K57.9", "K58",
                        "K58.0", "K59.1", "K60.3", "K61.0", "K61.2", "K62.1", "K62.5",
                        "K63", "K63.1", "K63.5", "K64", "K64.2", "K64.3", "K64.8",
                        "K65", "K71.2", "K71.6", "K72.0", "K72.2", "K73", "K74",
                        "K74.0", "K74.1", "K74.2", "K74.6", "K75.8", "K77", "K78.6",
                        "K80", "K80.0", "K80.1", "K80.2", "K80.3", "K80.4", "K80.8",
                        "K81", "K81.0", "K83", "K83.0", "K85", "K85.0", "K85.8",
                        "K85.9", "K86.1", "K92", "K92.2", "K92.8", "K92.9")
genitourinary_diseases <- c("N00", "N13.2", "N13.3", "N13.6", "N17", "N17.9", "N18",
                            "N18.4", "N18.5", "N18.9", "N19", "N20", "N20.0", "N20.1",
                            "N20.1, N23, N20.0, K21, M47", "N20.2", "N21.0", "N21.1",
                            "N23", "N28", "N30.0", "N30.8", "N32.0", "N34.1", "N39.0",
                            "N40", "N43.2", "N45", "N47", "N48.1", "N70")
```

The anti-microbials categories:

```{r}
cefoperazone <- c("Cefoperazol","Cefoperazole", "Cefoperazon", "Cefoperazone")
ampicill_sulb <- "Senitram"
cefamandol <- c("Cefamandol", "Cefemandol")
cefo_sulb <- "Vitabactam"
cefazolin <- "Cefazolin"
cefprozil <- "Cefprozil"
cefradin <- "Cefradin"
ceftizoxime <- c("Ceftizoxim", "Ceftizoxime", "Ceftizoxom", "Ceftrizoxim")
cefmetazol <- "Cefmetazol"
ticarcillin_acid_clavulan <- c("Ticarcillin + Acid clavulanic",
                               "Ticarcillin + Clavulanic",
                               "Ticarcillin/acid clavulanic")
```

Number of seconds in 1 day:

```{r}
spd <- 86400
```

The path to the data folder:

```{r constants}
if (grepl("arc|hoisy", Sys.getenv("USER"))) {
  path2data <- paste0("~/Library/CloudStorage/OneDrive-OxfordUniversityClinical",
                      "ResearchUnit/GitHub/HuongVTL/CRE-gut-acquisition/")
} else {
  path2data <- paste("C:/Users/huongvtl/OneDrive - Oxford University Clinical",
                     "Research Unit/60HN CRE transmission manuscript/")
}
```


## Packages

Required packages:

```{r}
required <- c("gmodels", "lsmeans", "lme4", "glmmLasso", "stringr", "magrittr",
              "readxl", "rlang", "tidyr", "purrr", "dplyr")
```

Installing those that are not installed yet:

```{r}
to_install <- required[! required %in% installed.packages()[,"Package"]]
if (length(to_install)) install.packages(to_install)
```

Loading the packages for interactive use:

```{r warning = FALSE, message = FALSE}
invisible(sapply(required, library, character.only = TRUE))
```


## Functions

Not in:

```{r}
"%ni%" <- Negate("%in%")
```

A function that adds the path of the data folder to a file name:

```{r}
make_path <- function(file) paste0(path2data, file)
```

Tuning `read_excel()`:

```{r}
read_excel2 <- function(file, ...) read_excel(make_path(file), ...)
```

Tuning the `merge()` function:

```{r}
merge2 <- function(...) merge(..., by = "USUBJID", all = TRUE)
```

Tuning the `difftime()` function:

```{r}
duration <- function(from, to) difftime(to, from, units = "days") + 1
```

Tuning the `starts_with()` function:

```{r}
starts_with2 <- function(...) starts_with(..., ignore.case = FALSE)
```


## CRF data

Loading the CRF data:

```{r}
CRF <- c("SCR", "ADM", "DEMO_HIS", "DEMO_HIS_HISTORY_GRID", "DIS", "ANT",
         "ANT_ANB_HOSP_GRID") |> 
  set_names() |> 
  map(read_excel2, file = CRF_file) |>
  map(filter, entry == 2)
```

**Note:** whereas all the non `*GRID* tab have only 1 observation per patient, all the
*GRID* do have or can have more than one observation per patient:

```{r}
map(CRF, ~ sort(unique(table(.x$USUBJID))))
```

Discharge dates of those who did not provide any sample at discharge:

```{r}
discharge_date <- no_sample_discharge_dates |>
  read_excel2() |> 
  select(USUBJID, `Discharge date`)
```


### Tests

On diseases categories:

```{r}
unique_codes <- unique(CRF$DIS$FINAL_DIAG_ICD10)
all_codes <- c(id_intestinal, id_other, neoplasms, circulatory_diseases,
               respiratory_diseases, digestive_diseases, genitourinary_diseases)

all_codes |> 
  table() |> 
  unique()

all(all_codes %in% unique_codes)
setdiff(all_codes, unique_codes)
```

On antibiotics categories:

```{r}
unique_ab <- unique(CRF$ANT_ANB_HOSP_GRID$ANB_OTHER_SPEC)
all_ab <- c(cefoperazone, ampicill_sulb, cefamandol, cefo_sulb,
            cefazolin, cefprozil, cefradin, ceftizoxime, cefmetazol,
            ticarcillin_acid_clavulan)

all_ab |> 
  table() |> 
  unique()

all(all_ab %in% unique_ab)
setdiff(all_ab, unique_ab)
```


### Reformatting

The `SCR` tab (screening data) patched with the dates of discharge of the patients who
did not provide any sample at discharge:

```{r}
CRF$SCR <- CRF$SCR |>
  select(USUBJID, SPEC_DATE_DISCHARGE) |> 
  left_join(discharge_date, "USUBJID") |> 
  mutate(DISCHARGE_DATE = coalesce(SPEC_DATE_DISCHARGE, `Discharge date`)) |>
  select(USUBJID, DISCHARGE_DATE)
```

The `ADM` tab (admission data):

```{r}
CRF$ADM <- CRF$ADM |> 
  select(USUBJID, SITEID, YEAR_BIRTH, GENDER, ADMISSION_DATE, WARD_3, CORMOBIDITY,
         MI_HIS, CHF, PVD, CVD, DEMENTIA, CPD, CTD, PUD, MILD_LIVER, SEV_LIVER,
         HEMIPLEGIA, SEV_RENAL, starts_with("DIAB"), TUMOR_NOMETA, LEUKEMIA, LYMPHOMA,
         META_TUMOR, ANB_ADMISSION) |> 
  mutate(hospitaltype = ifelse(SITEID %in% c("010", "159"), "provincial", "district"),
         age = 2025 - YEAR_BIRTH + 1,
         Ab_history = ANB_ADMISSION %in% c(1, 4), # 1: No; 4: Don't know
         wardtype = ifelse(WARD_3, "surgical", "medical/ID")) |>
  select(-YEAR_BIRTH, -ANB_ADMISSION, -WARD_3)
```

The `DEMO_HIS` tab (demographic and historical information):

```{r}
CRF$DEMO_HIS <- CRF$DEMO_HIS |> 
  select(USUBJID, MARITAL, starts_with("JOB"), ADULT, CHILDREN, AMBULATORY, SMOKING,
         starts_with("ALCOHOL"), starts_with("DRUG")) |> 
  mutate(job = JOB_SPECIFY |>
           case_match(c("Cán bộ công chức", "Cán bộ xã") ~ 1,
                      c("Bảo vệ", "Cơ khí","Hộ lý", "Lái tàu thủy", "Lao động tự do",
                        "Vệ sỹ") ~ 4,
                      c("già", "Già", "Hết độ tuổi lao động") ~ 8,
                      c("Ở nhà", "Tự do") ~ 9, .default = as.numeric(JOB)) |> 
           case_match(6 ~ "farmer", 7 ~ "housewife", 8 ~ "retired",
                      .default = "all other jobs"),
         householdsize = ADULT + CHILDREN,
         smoking = case_match(SMOKING, "1" ~ "current smoker",
                                       "2" ~ "former smoker",
                                       .default = "all non-smokers"),
         children = CHILDREN > 0,
         married = MARITAL < 2,
         independent = AMBULATORY < 2,
         across(starts_with(c("ALCOHOL", "DRUG")), as.integer),
         alcohol_problem = ALCOHOL_CUTDOWN + ALCOHOL_ANNOYED + ALCOHOL_GUILTY +
           ALCOHOL_DRUG > 4,
         drug_problem = DRUG_CUTDOWN + DRUG_ANNOYED + DRUG_GUILTY + DRUG_DRUG > 4) |> 
  select(-MARITAL, -starts_with2("JOB"), -ADULT, -CHILDREN, -AMBULATORY, -SMOKING,
         -starts_with2("ALCOHOL"), -starts_with2("DRUG"))
```

The `DEMO_HIS_HISTORY_GRID` tab (history data per type of history):

```{r}
CRF$DEMO_HIS_HISTORY_GRID <- CRF$DEMO_HIS_HISTORY_GRID |>
  select(USUBJID, HIS_CONDITION, HIS_YN) |> 
  mutate(across(HIS_YN, ~ .x > 1),
         across(HIS_CONDITION, ~ c("InvasiveHistory",
                                   "MedicationHistory", "TravelHistory",
                                   "HealthcareHistory")[as.integer(.x)])) |> 
  pivot_wider(names_from = HIS_CONDITION, values_from = HIS_YN)
```

The `DIS` tab (discharge data):

```{r}
CRF$DIS <- CRF$DIS |>
  select(USUBJID, DISCHARGE, FINAL_DIAG_ICD10, ICU, CVC, PVC, UC, IID,
         ends_with(c("TO", "FROM"))) |> 
  mutate(ICDGroup = case_match(FINAL_DIAG_ICD10,
                               id_intestinal          ~ "ID (Intestinal)",
                               id_other               ~ "ID (Other)",
                               neoplasms              ~ "Neoplasms",
                               circulatory_diseases   ~ "Circulatory diseases",
                               respiratory_diseases   ~ "Respiratory diseases",
                               digestive_diseases     ~ "Digestive diseases",
                               genitourinary_diseases ~ "Genitourinary diseases",
                               .default = "Other"),
         ICUduration = duration(ICU_FROM, ICU_TO),
         CVCduration = duration(CVC_FROM, CVC_TO),
         PVCduration = duration(PVC_FROM, PVC_TO),
         UCduration  = duration( UC_FROM,  UC_TO),
         IIDduration = duration(IID_FROM, IID_TO)) |> 
  select(-FINAL_DIAG_ICD10, -ends_with(c("TO", "FROM")))
```

The `ANT` tab (antibiotic data):

```{r}
CRF$ANT <- CRF$ANT |>
  select(USUBJID, ANB_HOS) |> 
  mutate(across(ANB_HOS, ~ .x > 2))
```

The `ANT_ANB_HOSP_GRID` tab (antibiotic data per antibiotic):

```{r}
CRF$ANT_ANB_HOSP_GRID <- CRF$ANT_ANB_HOSP_GRID |>
  select(USUBJID, ANB_HOSP_NAME, ANB_OTHER_SPEC, ANB_HOSP_START_DATE,
         ANB_HOSP_END_DATE) |> 
  mutate(agent = case_match(ANB_OTHER_SPEC,
                            cefoperazone              ~ "Cefoperazone",
                            ampicill_sulb             ~ "Ampicillin_sulbactam",
                            cefamandol                ~ "Cefamandol",
                            cefo_sulb                 ~ "Cefoperazon_sulbactam",
                            cefazolin                 ~ "Cefazolin",
                            cefprozil                 ~ "Cefprozil",
                            cefradin                  ~ "Cefradin",
                            ceftizoxime               ~ "Ceftizoxime",
                            cefmetazol                ~ "Cefmetazol",
                            ticarcillin_acid_clavulan ~ "Ticarcillin/acid clavulanic",
                            .default = ANB_HOSP_NAME),
         DOT = as.numeric((ANB_HOSP_END_DATE - ANB_HOSP_START_DATE) / spd + 1)) |> 
  group_by(USUBJID, agent) |> 
  summarise(DOT = sum(DOT), .groups = "drop") |> 
  pivot_wider(names_from = agent, values_from = DOT) |> 
  mutate(across(everything(), ~ replace_na(.x, 0)),
         DOT = rowSums(across(where(is.numeric))))
```

Note that now we have only one row per patient for all the slots:

```{r}
map(CRF, ~ sort(unique(table(.x$USUBJID))))
```

Merging all the CRF data:

```{r}
all_data <- CRF |>
  reduce(merge2) |> 
  mutate(los = as.numeric((as.POSIXct(DISCHARGE_DATE) -
                             as.POSIXct(ADMISSION_DATE)) / spd + 1)) |>
  select(-DISCHARGE_DATE, -ADMISSION_DATE) |> 
  mutate(across(c(where(is.numeric), -c(hospitaltype, age, Ab_history, householdsize)),
                ~ replace_na(.x, 0)))
```


## MALDI-TOF data

Reading the data sets:

```{r load data}
MALDI_TOF <- malditof_file |>
  read_excel2() |> 
  filter(Identification_MALDITOF %ni% non_CRE) |> 
  select(USUBJID, SPEC_DATE, SampleSchedule, Identification_MALDITOF) |> 
  unique()
```

```{r cre carriage and species}
#CRE_admission <- subset(cre, cre$SampleSchedule == "ADMISSION"); 
#CRE_discharge <- subset(cre, cre$SampleSchedule == "DISCHARGE")
#
#length(unique(CRE_admission$USUBJID))
#length(unique(CRE_discharge$USUBJID))
#
### subset to specific CREC or CRKP
#CREC_admission <- CRE_admission %>%
#  filter(Identification_MALDITOF == "Escherichia coli")
#
#CREC_discharge <- CRE_discharge %>%
#  filter(Identification_MALDITOF == "Escherichia coli")
#
#CRKP_admission <- CRE_admission %>%
#  filter(Identification_MALDITOF == "Klebsiella pneumoniae")
#
#CRKP_discharge <- CRE_discharge %>%
#  filter(Identification_MALDITOF == "Klebsiella pneumoniae")
```

```{r}
#merge2(all_data, CREC_admission)
```


## Risk data

Preparing the risk data:

```{r}
risk_data <- all_data |> 
  mutate(across(smoking, ~ .x != "all non-smokers"),
         across(children, ~ replace_na(.x, "no children in the household")),
         across(job, ~ ifelse(.x == "all other jobs", "all_others", .x)),
         across(ICDGroup, ~ ifelse(.x %in% c("Circulatory diseases",
                                             "Genitourinary diseases",
                                             "ID (Intestinal)"), "all_others", .x)),
         heart_disease = MI_HIS | CHF,
         vascular_disease = CVD | PVD,
         cancer = TUMOR_NOMETA | LEUKEMIA | LYMPHOMA | META_TUMOR)
```

A function that makes a data set for a specific set of bacteria:

```{r}
make_data <- function(bacteria = "all") {
  if (bacteria != "all")
    MALDI_TOF <- filter(MALDI_TOF, Identification_MALDITOF %in% bacteria)
  
  MALDI_TOF |> 
    filter(SampleSchedule == "ADMISSION") |> 
    select(USUBJID) |>
    unique() |> 
    mutate(carrier = TRUE) %>% 
    left_join(risk_data, ., "USUBJID") |> 
    mutate(across(carrier, ~ replace_na(.x, FALSE)))
}
```


## Prepare variables for Lasso modeling

```{r}
dataset <- make_data("Escherichia coli")
```

```{r}
dataset
```








```{r scaling and fixing data for Lasso}
# standardize predictor variables before Lasso regression because the penalty is
# applied to the magnitude of coefficients; standardizing (to mean 0, std dev 1)
# ensures all variables are treated equally, allowing for meaningful coefficient
# comparison and selection based on true predictive power, not scale. Check Defaults:
# Confirm glmmLassoControl settings; standardize = TRUE is the standard for 2026 to
# ensure the L1 penalty is consistent. Factor Recognition: Ensure categorical variables
# are recognized as factors so the algorithm can apply group-wise updates. 

#for continuous variables - check if re-scaled back when interpreting

riskdata_scaled <- riskdata %>% 
  mutate(age_s = scale(age), 
         across(c(GENDER, SITEID, CORMOBIDITY, DEMENTIA, CPD, CTD, PUD, MILD_LIVER,
                  SEV_LIVER, HEMIPLEGIA, SEV_RENAL, DIAB_NOEOD, DIAB_EOD),
                as.factor)) |> 
  select(CRE_carriage, age_s, GENDER, smoking2, SITEID, children2, married, ambulatory,
         job_farmer, job_housewife, job_retired, CORMOBIDITY, heart_diseases,
         vascular_diseases, DEMENTIA, CPD, CTD, PUD, MILD_LIVER, SEV_LIVER, HEMIPLEGIA,
         SEV_RENAL, DIAB_NOEOD, DIAB_EOD, cancer, alcohol, drug, wardtype, Ab_history,
         InvasiveHistory, MedicationHistory, HealthcareHistory, hospitaltype,
         `Circulatory diseases`, `Genitourinary diseases`, `ID (Intestinal)`,
         `ID (Other)`, Neoplasms, `Respiratory diseases`, `Digestive diseases`)
#         gender = as.factor(GENDER),
#         hospital = as.factor(SITEID),
#         cormobidity = as.factor(CORMOBIDITY),
#         dementia = as.factor(DEMENTIA),
#         cpd = as.factor(CPD),
#         ctd = as.factor(CTD),
#         pud = as.factor(PUD),
#         mild_liver = as.factor(MILD_LIVER),
#         sev_liver = as.factor(SEV_LIVER),
#         hemiplegia = as.factor(HEMIPLEGIA),
#         sev_renal = as.factor(SEV_RENAL),
#         diabetes_noeod = as.factor(DIAB_NOEOD),
#         diabetes_eod = as.factor(DIAB_EOD),

#no patient has AIDS, also not include pvd as no cases have pvd

data_clean <- na.exclude(riskdata_scaled)
nrow(riskdata_scaled) - nrow(data_clean) # Check how many rows you lost
```


## Fit a simple glmm model

```{r fit a simple model glmm}
mixed_formula <- CRE_carriage ~ age_s + GENDER + smoking2 + children2 + married +
  ambulatory + job_farmer + job_housewife + job_retired + CORMOBIDITY + 
  vascular_diseases + CPD + CTD + PUD + MILD_LIVER + SEV_LIVER + HEMIPLEGIA +
  SEV_RENAL + DIAB_NOEOD + DIAB_EOD + cancer + alcohol + drug + wardtype +
  InvasiveHistory + MedicationHistory + HealthcareHistory + hospitaltype + Ab_history +
  `Circulatory diseases` + `Genitourinary diseases` + `ID (Intestinal)` +
  `ID (Other)` + Neoplasms + `Respiratory diseases` + `Digestive diseases` +
  (1| SITEID)                           # not include heart_diseases and dementia yet -


simple_mixed_model <- glmer(mixed_formula, data_clean, binomial(link = "logit"))
summary(simple_mixed_model)
initial_fixed_estimates <- fixef(simple_mixed_model)
initial_random_estimates <- ranef(simple_mixed_model)
Delta.start <- c(as.numeric(initial_fixed_estimates), rep(0, 100),
                 as.numeric(initial_random_estimates))
Q.start <- as.numeric(VarCorr(simple_mixed_model))
```


## Find the best lambda for glmmLasso

```{r find best lambda for glmmLasso}
# Define a sequence of lambda values (from high penalty to low)
lambda_seq <- seq(10, 0, by = -.1)

#fixed formula
fixed_formula <- update(mixed_formula, . ~ . - (1| SITEID))

# Initialize a vector to store BIC or AIC values
baic_vec <- rep(Inf, length(lambda_seq))

# Create a loop to test each lambda
for(j in 1:length(lambda_seq)) {
  print(paste("Testing Lambda:", lambda_seq[j]))
  #Use try() to prevent the loop from breaking if one model fails to converge
  glmm_temp <- try(glmmLasso(
    fix = fixed_formula,
    rnd = list(hospital = ~1),
    data = data_clean,
    lambda = lambda_seq[j],
    family = binomial(),
    switch.NR = TRUE,
    final.re = FALSE,
    control = list(start = Delta.start, q_start = Q.start)),
    silent = TRUE)
  #If the model fit successfully, save the BIC
  if (!inherits(glmm_temp, "try-error")) baic_vec[j] <- glmm_temp$bic
}

# Find the lambda that produced the lowest BIC
(opt_lambda <- lambda_seq[which.min(baic_vec)])
baic_vec
lambda_seq[which(is.infinite(baic_vec))]
```


## Fit the final Lasso model

```{r fit model}
CRE_admission_model <- glmmLasso(
  fix = fixed_formula,
  rnd = list(hospital = ~1),
  data = data_clean,
  lambda = opt_lambda, # larger -> stronger regularization and more coefficients shrunk to zero; smaller reduces penalty
  family = binomial(link = logit),
  switch.NR = FALSE, # switch to the faster Newton-Raphson method to speed up model fitting process
  final.re = TRUE,
  control = list(start = Delta.start, q_start = Q.start))

(model_summary <- summary(CRE_admission_model))
```


## Final estimates

``` {r extract ORs and 95%CI}
std_errors <- model_summary$coefficients[, "StdErr"]; 
tab <- cbind(Est = coef(CRE_admission_model),
             LL = coef(CRE_admission_model) - 1.96 * std_errors,
             UL = coef(CRE_admission_model) + 1.96 * std_errors); 
round(cbind(exp(tab), p = coef(summary(CRE_admission_model))[, 4]), digits = 3) #p-value
```
                                 