---
title: "CRE Admission Risk Factors BRMS MODEL"
format: html
toc: TRUE
toc_depth: 2
number_sections: TRUE
toc_float:
collapsed: no
smooth_scroll: yes
editor: visual
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(cache.path = 'C:/Users/huongvtl/OneDrive - Oxford University Clinical Research Unit/60HN CRE transmission manuscript/cache')
```

## Constants

CRF file:

```{r}
CRF_file <- "16-12-2025-_60HN_PATIENT_P1_Data.xls"
```

MALDI-TOF file:

```{r}
malditof_file <- "60HN_ID_MALDITOF_confirmation_20251128.xlsx"
```

The dates of discharge of the patients who did no provide any sample at discharge:

```{r}
no_sample_discharge_dates <- "60HN - DischargeDate_no_discharge_sample_27Nov25.xlsx"
```

Bacteria to exclude from the analysis:

```{r}
non_CRE <- c("Acinetobacter baumannii", "Aeromonas caviae", "Aeromonas hydrophila",
             "Aeromonas veronii", "Enterococcus faecium", "Cupriavidus gilardii",
             "Pseudomonas putida")
```

The diseases categories:

```{r}
id_intestinal <- c("A04", "A04.8", "A04.9", "A05.9", "A06.4", "A08.0", "A08.5", "A09",
                   "A09.0", "A09.9")
id_other <- c("A15.0", "A15.3", "A16.2", "A41", "A41.5", "A41.8", "A41.9", "A48",
              "A49.9", "A79.8", "A79.9", "A93", "A94", "A97", "B00.1", "B01", "B01.2",
              "B01.8", "B02", "B02.7", "B02.8", "B05", "B05.2", "B05.8", "B05.9",
              "B17", "B18.1", "B18.2", "B34.9", "B83.8")
neoplasms <- c("C18", "C18.9; K56.6", "C20", "C22", "C22.9", "C34.9", "C41", "C61",
               "C67.9", "C70.0", "C91.9", "C92.2", "C95.0", "D12.0", "D17", "D21",
               "D21.9", "D23", "D23.9", "D27", "D37.4", "D38.1", "D40.0", "D44.0",
               "D48.1")
circulatory_diseases <- c("I10", "I10-E11-E25-I69", "I10; H81", "I11.9", "I12.5",
                          "I18", "I20", "I20.0", "I20.8", "I21", "I21.4", "I21.9",
                          "I24.0", "I25", "I25.2", "I25.5", "I48", "I48.0", "I48.2",
                          "I50", "I50.9", "I61", "I63", "I63.8", "I64", "I67",
                          "I67-I10", "I67 - I10", "I69.4", "I70.2", "I80", "I87.2",
                          "I88.8", "I92.9", "I95", "I99")
respiratory_diseases <- c("J01", "J01.9", "J02", "J02.9", "J04.0", "J06", "J06.9",
                          "J09", "J10.1", "J10.8", "J11", "J11.1", "J11.8", "J15",
                          "J15.9", "J16", "J17.1", "J18", "J18-I20.2", "J18.0",
                          "J18.1", "J18.8", "J18.9", "J20", "J20.9", "J40", "J42",
                          "J44", "J44.0", "J44.1", "J44.9", "J45", "J90", "J96.0",
                          "J96.9", "J96/18")
digestive_diseases <- c("K11.2", "K12.3", "K21", "K21.0", "K21.9", "K22.6", "K25",
                        "K25.0", "K25.3", "K25.9", "K26.0", "K27", "K27-J20", "K27.0",
                        "K27.3", "K27.9", "K29", "K29.0", "K29.1", "K29.2", "K29.6",
                        "K29.9", "K30", "K35", "K35.1", "K35.3", "K35.5", "K35.8",
                        "K35.9", "K36", "K40", "K40.9", "K42", "K50", "K52.3", "K52.9",
                        "K56", "K56.4", "K56.6", "K57.0", "K57.3", "K57.9", "K58",
                        "K58.0", "K59.1", "K60.3", "K61.0", "K61.2", "K62.1", "K62.5",
                        "K63", "K63.1", "K63.5", "K64", "K64.2", "K64.3", "K64.8",
                        "K65", "K71.2", "K71.6", "K72.0", "K72.2", "K73", "K74",
                        "K74.0", "K74.1", "K74.2", "K74.6", "K75.8", "K77", "K78.6",
                        "K80", "K80.0", "K80.1", "K80.2", "K80.3", "K80.4", "K80.8",
                        "K81", "K81.0", "K83", "K83.0", "K85", "K85.0", "K85.8",
                        "K85.9", "K86.1", "K92", "K92.2", "K92.8", "K92.9")
genitourinary_diseases <- c("N00", "N13.2", "N13.3", "N13.6", "N17", "N17.9", "N18",
                            "N18.4", "N18.5", "N18.9", "N19", "N20", "N20.0", "N20.1",
                            "N20.1, N23, N20.0, K21, M47", "N20.2", "N21.0", "N21.1",
                            "N23", "N28", "N30.0", "N30.8", "N32.0", "N34.1", "N39.0",
                            "N40", "N43.2", "N45", "N47", "N48.1", "N70")
```

The anti-microbials categories:

```{r}
cefoperazone <- c("Cefoperazol","Cefoperazole", "Cefoperazon", "Cefoperazone")
ampicill_sulb <- "Senitram"
cefamandol <- c("Cefamandol", "Cefemandol")
cefo_sulb <- "Vitabactam"
cefazolin <- "Cefazolin"
cefprozil <- "Cefprozil"
cefradin <- "Cefradin"
ceftizoxime <- c("Ceftizoxim", "Ceftizoxime", "Ceftizoxom", "Ceftrizoxim")
cefmetazol <- "Cefmetazol"
ticarcillin_acid_clavulan <- c("Ticarcillin + Acid clavulanic",
                               "Ticarcillin + Clavulanic",
                               "Ticarcillin/acid clavulanic")
```

Number of seconds in 1 day:

```{r}
spd <- 86400
```

The path to the data folder:

```{r constants}
if (grepl("arc|hoisy", Sys.getenv("USER"))) {
  path2data <- paste0("~/Library/CloudStorage/OneDrive-OxfordUniversityClinical",
                      "ResearchUnit/GitHub/HuongVTL/CRE-gut-acquisition/")
} else {
  path2data <- paste("C:/Users/huongvtl/OneDrive - Oxford University Clinical",
                     "Research Unit/60HN CRE transmission manuscript/")
}
```

## Packages

Required packages:

```{r message = FALSE}
required <- c("gmodels", "lsmeans", "lme4", "glmmLasso", "stringr", "magrittr",
              "readxl", "rlang", "tidyr", "purrr", "dplyr", "brms", "ggplot2", "tidyverse","tidybayes", "bayesplot", "loo", "posterior", "flextable", "officer")
```

Installing those that are not installed yet:

```{r}
to_install <- required[! required %in% installed.packages()[,"Package"]]
if (length(to_install)) install.packages(to_install)
```

Loading the packages for interactive use:

```{r warning = FALSE, message = FALSE}
invisible(sapply(required, library, character.only = TRUE))
```

## Functions

Not in:

```{r}
"%ni%" <- Negate("%in%")
```

A function that adds the path of the data folder to a file name:

```{r}
make_path <- function(file) paste0(path2data, file)
```

Tuning `read_excel()`:

```{r}
read_excel2 <- function(file, ...) read_excel(make_path(file), ...)
```

Tuning the `merge()` function:

```{r}
merge2 <- function(...) merge(..., by = "USUBJID", all = TRUE)
```

Tuning the `difftime()` function:

```{r}
duration <- function(from, to) difftime(to, from, units = "days") + 1
```

Tuning the `starts_with()` function:

```{r}
starts_with2 <- function(...) starts_with(..., ignore.case = FALSE)
```

## CRF data

Loading the CRF data:

```{r}
CRF <- c("SCR", "ADM", "DEMO_HIS", "DEMO_HIS_HISTORY_GRID", "DIS", "ANT",
         "ANT_ANB_HOSP_GRID") |> 
  set_names() |> 
  map(read_excel2, file = CRF_file) |>
  map(filter, entry == 2)
```

**Note:** whereas all the non \`*GRID* tab have only 1 observation per patient, all the *GRID* do have or can have more than one observation per patient:

```{r}
map(CRF, ~ sort(unique(table(.x$USUBJID))))
```

Discharge dates of those who did not provide any sample at discharge:

```{r}
discharge_date <- no_sample_discharge_dates |>
  read_excel2() |> 
  select(USUBJID, `Discharge date`)
```

### Tests

On diseases categories:

```{r}
unique_codes <- unique(CRF$DIS$FINAL_DIAG_ICD10)
all_codes <- c(id_intestinal, id_other, neoplasms, circulatory_diseases,
               respiratory_diseases, digestive_diseases, genitourinary_diseases)

all_codes |> 
  table() |> 
  unique()

all(all_codes %in% unique_codes)
setdiff(all_codes, unique_codes)
```

On antibiotics categories:

```{r}
unique_ab <- unique(CRF$ANT_ANB_HOSP_GRID$ANB_OTHER_SPEC)
all_ab <- c(cefoperazone, ampicill_sulb, cefamandol, cefo_sulb,
            cefazolin, cefprozil, cefradin, ceftizoxime, cefmetazol,
            ticarcillin_acid_clavulan)

all_ab |> 
  table() |> 
  unique()

all(all_ab %in% unique_ab)
setdiff(all_ab, unique_ab)
```

### Reformatting

The `SCR` tab (screening data) patched with the dates of discharge of the patients who did not provide any sample at discharge:

```{r}
CRF$SCR <- CRF$SCR |>
  select(USUBJID, SPEC_DATE_DISCHARGE) |> 
  left_join(discharge_date, "USUBJID") |> 
  mutate(DISCHARGE_DATE = coalesce(SPEC_DATE_DISCHARGE, `Discharge date`)) |>
  select(USUBJID, DISCHARGE_DATE)
```

The `ADM` tab (admission data, note the choice made on `Ab_history`):

```{r}
CRF$ADM <- CRF$ADM |> 
  select(USUBJID, SITEID, YEAR_BIRTH, GENDER, ADMISSION_DATE, WARD_3, CORMOBIDITY,
         MI_HIS, CHF, PVD, CVD, DEMENTIA, CPD, CTD, PUD, MILD_LIVER, SEV_LIVER,
         HEMIPLEGIA, SEV_RENAL, starts_with("DIAB"), TUMOR_NOMETA, LEUKEMIA, LYMPHOMA,
         META_TUMOR, ANB_ADMISSION) |> 
  mutate(hospitaltype = ifelse(SITEID %in% c("010", "159"), "provincial", "district"),
         age = 2025 - YEAR_BIRTH + 1,
         Ab_history = ANB_ADMISSION %ni% c(1, 4),  # 1: No; 4: Don't know
         wardtype = ifelse(WARD_3, "surgical", "medical/ID"),
         across(GENDER, ~ c("male", "female")[as.integer(.x)]),
         across(CORMOBIDITY, ~ .x > 1)) |>
  select(-YEAR_BIRTH, -ANB_ADMISSION, -WARD_3)
```

The `DEMO_HIS` tab (demographic and historical information, note the choice made on `smoking`):

```{r}
CRF$DEMO_HIS <- CRF$DEMO_HIS |> 
  select(USUBJID, MARITAL, starts_with("JOB"), ADULT, CHILDREN, AMBULATORY, SMOKING,
         starts_with("ALCOHOL"), starts_with("DRUG")) |> 
  mutate(job = JOB_SPECIFY |>
           case_match(c("Cán bộ công chức", "Cán bộ xã") ~ 1,
                      c("Bảo vệ", "Cơ khí","Hộ lý", "Lái tàu thủy", "Lao động tự do",
                        "Vệ sỹ") ~ 4,
                      c("già", "Già", "Hết độ tuổi lao động") ~ 8,
                      c("Ở nhà", "Tự do") ~ 9, .default = as.numeric(JOB)) |> 
           case_match(6 ~ "farmer", 7 ~ "housewife", 8 ~ "retired",
                      .default = "all_others"),
         householdsize = ADULT + CHILDREN,
         smoking = case_match(SMOKING, "1" ~ "current smoker",
                                       "2" ~ "former smoker",
                                       .default = "all non-smokers"), # contains "status unknown" too
         children = CHILDREN > 0,
         married = MARITAL < 2,
         independent = AMBULATORY < 2,
         across(starts_with(c("ALCOHOL", "DRUG")), as.integer),
         alcohol_problem = ALCOHOL_CUTDOWN + ALCOHOL_ANNOYED + ALCOHOL_GUILTY +
           ALCOHOL_DRUG > 4,
         drug_problem = DRUG_CUTDOWN + DRUG_ANNOYED + DRUG_GUILTY + DRUG_DRUG > 4) |> 
  select(-MARITAL, -starts_with2("JOB"), -ADULT, -CHILDREN, -AMBULATORY, -SMOKING,
         -starts_with2("ALCOHOL"), -starts_with2("DRUG"))
```

The `DEMO_HIS_HISTORY_GRID` tab (history data per type of history):

```{r}
CRF$DEMO_HIS_HISTORY_GRID <- CRF$DEMO_HIS_HISTORY_GRID |>
  select(USUBJID, HIS_CONDITION, HIS_YN) |> 
  mutate(across(HIS_YN, ~ .x > 1),
         across(HIS_CONDITION, ~ c("InvasiveHistory",
                                   "MedicationHistory", "TravelHistory",
                                   "HealthcareHistory")[as.integer(.x)])) |> 
  pivot_wider(names_from = HIS_CONDITION, values_from = HIS_YN)
```

The `DIS` tab (discharge data):

```{r}
CRF$DIS <- CRF$DIS |>
  select(USUBJID, DISCHARGE, FINAL_DIAG_ICD10, ICU, CVC, PVC, UC, IID,
         ends_with(c("TO", "FROM"))) |> 
  mutate(ICDGroup = case_match(FINAL_DIAG_ICD10,
                               id_intestinal          ~ "ID (Intestinal)",
                               id_other               ~ "ID (Other)",
                               neoplasms              ~ "Neoplasms",
                               circulatory_diseases   ~ "Circulatory diseases",
                               respiratory_diseases   ~ "Respiratory diseases",
                               digestive_diseases     ~ "Digestive diseases",
                               genitourinary_diseases ~ "Genitourinary diseases",
                               .default = "Other"),
         ICUduration = duration(ICU_FROM, ICU_TO),
         CVCduration = duration(CVC_FROM, CVC_TO),
         PVCduration = duration(PVC_FROM, PVC_TO),
         UCduration  = duration( UC_FROM,  UC_TO),
         IIDduration = duration(IID_FROM, IID_TO)) |> 
  select(-FINAL_DIAG_ICD10, -ends_with(c("TO", "FROM")))
```

The `ANT` tab (antibiotic data):

```{r}
CRF$ANT <- CRF$ANT |>
  select(USUBJID, ANB_HOS) |> 
  mutate(across(ANB_HOS, ~ .x > 2))
```

The `ANT_ANB_HOSP_GRID` tab (antibiotic data per antibiotic):

```{r}
CRF$ANT_ANB_HOSP_GRID <- CRF$ANT_ANB_HOSP_GRID |>
  select(USUBJID, ANB_HOSP_NAME, ANB_OTHER_SPEC, ANB_HOSP_START_DATE,
         ANB_HOSP_END_DATE) |> 
  mutate(agent = case_match(ANB_OTHER_SPEC,
                            cefoperazone              ~ "Cefoperazone",
                            ampicill_sulb             ~ "Ampicillin_sulbactam",
                            cefamandol                ~ "Cefamandol",
                            cefo_sulb                 ~ "Cefoperazon_sulbactam",
                            cefazolin                 ~ "Cefazolin",
                            cefprozil                 ~ "Cefprozil",
                            cefradin                  ~ "Cefradin",
                            ceftizoxime               ~ "Ceftizoxime",
                            cefmetazol                ~ "Cefmetazol",
                            ticarcillin_acid_clavulan ~ "Ticarcillin/acid clavulanic",
                            .default = ANB_HOSP_NAME),
         DOT = as.numeric((ANB_HOSP_END_DATE - ANB_HOSP_START_DATE) / spd + 1)) |> 
  group_by(USUBJID, agent) |> 
  summarise(DOT = sum(DOT), .groups = "drop") |> 
  pivot_wider(names_from = agent, values_from = DOT) |> 
  mutate(across(everything(), ~ replace_na(.x, 0)),
         DOT = rowSums(across(where(is.numeric))))
```

Note that now we have only one row per patient for all the slots:

```{r}
map(CRF, ~ sort(unique(table(.x$USUBJID))))
```

Merging all the CRF data:

```{r}
CRF2 <- CRF |>
  reduce(merge2) |> 
  mutate(los = as.numeric((as.POSIXct(DISCHARGE_DATE) -
                             as.POSIXct(ADMISSION_DATE)) / spd + 1)) |>
  select(-DISCHARGE_DATE, -ADMISSION_DATE) |> 
  mutate(across(c(where(is.numeric), -c(hospitaltype, age, Ab_history, householdsize)),
                ~ replace_na(.x, 0)))
```

## MALDI-TOF data

Reading the data sets:

```{r load data}
MALDI_TOF <- malditof_file |>
  read_excel2() |> 
  filter(Identification_MALDITOF %ni% non_CRE) |> 
  select(USUBJID, SPEC_DATE, SampleSchedule, Identification_MALDITOF) |> 
  unique()
```

## Risk data

Preparing the risk data:

```{r}
risk_data <- CRF2 |> 
  mutate(across(smoking, ~ .x != "all non-smokers"),
         across(children, ~ replace_na(.x, FALSE)),
         heart_disease = MI_HIS | CHF,
         vascular_disease = CVD | PVD,
         cancer = TUMOR_NOMETA | LEUKEMIA | LYMPHOMA | META_TUMOR) |> 
  select(-c(MI_HIS, CHF, CVD, PVD, TUMOR_NOMETA, LEUKEMIA, LYMPHOMA, META_TUMOR))
```

A function that makes a data set for a specific set of bacteria:

```{r}
make_data <- function(bacteria = "all") {
  if (bacteria != "all")
    MALDI_TOF <- filter(MALDI_TOF, Identification_MALDITOF %in% bacteria)
  
  MALDI_TOF |> 
    filter(SampleSchedule == "ADMISSION") |> 
    select(USUBJID) |>
    unique() |> 
    mutate(carrier = TRUE) %>% 
    left_join(risk_data, ., "USUBJID") |> 
    mutate(across(carrier, ~ replace_na(.x, FALSE))) |> 
    select(SITEID, carrier, age, GENDER, smoking, children, married, independent, job,
           CORMOBIDITY, 
           vascular_disease, cancer, CPD, CTD, PUD, MILD_LIVER, SEV_LIVER,
           HEMIPLEGIA, SEV_RENAL, DIAB_NOEOD, DIAB_EOD, 
           alcohol_problem, drug_problem,
           ICDGroup,
           hospitaltype, wardtype, InvasiveHistory, MedicationHistory,
           HealthcareHistory, Ab_history)
}
```

# Covariates

```{r}
predictors_full <- c(
  "age", "GENDER", "smoking", "children", "married", "independent", "job",
  "CORMOBIDITY", "vascular_disease", "cancer", "CPD", "CTD", "PUD", "MILD_LIVER", "SEV_LIVER", "HEMIPLEGIA", "SEV_RENAL", "DIAB_NOEOD", "DIAB_EOD", "alcohol_problem", "drug_problem", "hospitaltype", "wardtype", "InvasiveHistory", "MedicationHistory",
  "HealthcareHistory", "Ab_history", "ICDGroup"
  )

predictors_lean <- c(
  "age", "GENDER", "smoking", "children", "married", "job",
  "CORMOBIDITY", "CPD", "SEV_RENAL", "DIAB_EOD", "alcohol_problem", "drug_problem", "hospitaltype", "wardtype", "InvasiveHistory", "MedicationHistory",
  "HealthcareHistory", "Ab_history", "ICDGroup"
  )

rhs <- paste(predictors_lean, collapse = " + ")
```

# Klebsiella pneumoniae

## Mixed-effect logistic regression

```{r}
Kp_dataset <- "Klebsiella pneumoniae" |> 
make_data() |> 
as_tibble() |> 
na.exclude() |> 
mutate(across(where(~ !is.numeric(.x)), as.factor),
       age = as.numeric(scale(age)))

Kp_mixed_model <- glmer(carrier ~ age + GENDER + smoking + children + married + job + CORMOBIDITY + CPD + SEV_RENAL + DIAB_EOD + alcohol_problem + drug_problem + hospitaltype + wardtype + InvasiveHistory + MedicationHistory + HealthcareHistory + Ab_history + ICDGroup + (1 | SITEID),
                            Kp_dataset, binomial)
```

```{r}
summary(Kp_mixed_model)
```

For CRKP, the random effect **SITEID is not contributing** → the model is effectively **not multilevel.**

**–\> drop the random effect in brms model**

## Bayesian model in brms

### Check data distribution

```{r}
ggplot(make_data("Klebsiella pneumoniae"), aes(x = carrier)) +
  geom_bar(fill = "skyblue", color = "black") +
  labs(title = "Bernoulli Distribution of carriage status",
       x = "Carriage (0 = No, 1 = Yes)",
       y = "Count") +
  theme_minimal()



```

### Prepare for brms model

```{r}

# check names exist
stopifnot(all(predictors_full %in% names(Kp_dataset)))

#quick check on missing
missing_summary <- Kp_dataset %>% select(all_of(c("carrier", predictors_full, "SITEID"))) %>% summarise(across(everything(), ~ mean(is.na(.))))
View(missing_summary)


# Construct model formula with covariates

Kp_dataset <- Kp_dataset %>% mutate(carrier01 = as.integer(carrier == "TRUE"))
formula_brm <- as.formula(paste0("carrier01 ~ ", rhs))
```

### Run brms model with priors

```{r}

priors1 <- c(
  prior(normal(0, 1.5), class = "b"),        # coefficient shrinkage
  prior(normal(0, 1), class = "Intercept")
)

Kp_brms_model <- brms::brm(formula = formula_brm,
                        Kp_dataset, family = bernoulli(link = "logit"),
                        prior = priors1, 
                        chains = 3,
                        cores = parallel::detectCores(),
                        iter = 3000,  
                        warmup = 1000,
                        control = list(adapt_delta = 0.99, max_treedepth = 15),
                        seed = 2026)

summary(Kp_brms_model) 
```

### Convergence check

```{r}
sampler_diagnostics <- nuts_params(Kp_brms_model)

summary(Kp_brms_model)$fixed
rhat(Kp_brms_model)
neff_ratio(Kp_brms_model)

```

### Model checks

```{r}
pp_check(Kp_brms_model, ndraws = 200)   # posterior predictive check

loo_model <- loo(Kp_brms_model, moment_match = FALSE)
print(loo_model)

print(bayes_R2(Kp_brms_model))
```

### Posterior summaries

```{r}
post_summary <- posterior_summary(Kp_brms_model)
post_summary[grep("^b_", rownames(post_summary)), , drop = FALSE]  # show coefficients

# Posterior draws
draws <- as_draws_df(Kp_brms_model)

# Extract fixed effects only
beta_draws <- draws %>% select(starts_with("b_"))

# Convert to odds ratios
or_draws <- exp(beta_draws)

# Posterior summaries (median + 95% CrI)
or_summary <- apply(or_draws, 2, function(x)
  c(
    median = median(x),
    l95 = quantile(x, 0.025),
    u95 = quantile(x, 0.975)
  )
)

t(or_summary)
```

### Forest Plot

```{r}
#prepare data

# Get posterior summary (log-odds)
post <- posterior_summary(Kp_brms_model)

# Keep only fixed effects
post <- post[grep("^b_", rownames(post)), ]

# Convert to data frame
df_plot <- as.data.frame(post) %>%
  rownames_to_column("variable") %>%
  mutate(
    variable = gsub("^b_", "", variable),

    # Convert to odds ratios
    OR = exp(Estimate),
    OR_low = exp(Q2.5),
    OR_high = exp(Q97.5)
  )

#Clean variable names
df_plot <- df_plot %>%
  mutate(variable = recode(variable,
    age = "Age",
    GENDERmale = "Male sex",
    smokingTRUE = "Smoking",
    childrenTRUE = "Children in household",
    marriedTRUE = "Married",
    independentTRUE = "Independent",
    jobfarmer = "Farmer",
    jobhousewife = "Housewife",
    jobretired = "Retired",
    CORMOBIDITYTRUE = "Comorbidity",
    vascular_diseaseTRUE = "Vascular disease",
    cancerTRUE = "Cancer",
    CPDTRUE = "Chronic pulmonary disease",
    CTDTRUE = "Connective tissue disease",
    PUDTRUE = "Peptic ulcer disease",
    MILD_LIVERTRUE = "Mild liver disease",
    SEV_LIVERTRUE = "Severe liver disease",
    HEMIPLEGIATRUE = "Hemiplegia",
    SEV_RENALTRUE = "Severe renal disease",
    DIAB_NOEODTRUE = "Diabetes (no EOD)",
    DIAB_EODTRUE = "Diabetes (EOD)",
    alcohol_problemTRUE = "Alcohol use problem",
    drug_problemTRUE = "Drug use problem",
    hospitaltypeprovincial = "Provincial hospital",
    wardtypesurgical = "Surgical ward",
    InvasiveHistoryTRUE = "Invasive procedure history",
    MedicationHistoryTRUE = "Medication history (not antibiotic)",
    HealthcareHistoryTRUE = "Prior hospitalization",
    Ab_historyTRUE = "Prior antibiotic use",
    ICDGroupDigestivediseases = "Digestive diseases diagnosis",
    ICDGroupGenitourinarydiseases = "Genitourinary diseases diagnosis",
    ICDGroupIDIntestinal = "Intestinal Infectious diseases diagnosis",
    ICDGroupIDOther = "Other Infectious diseases diagnosis",
    ICDGroupNeoplasms = "Neoplasms diagnosis",
    ICDGroupOther = "Other diagnosis",
    ICDGroupRespiratorydiseases = "Respiratory diseases diagnosis"
  ))

# Order variables
df_plot <- df_plot %>%
  arrange(desc(OR)) %>%
  mutate(variable = factor(variable, levels = variable))

# Create plot
library(ggplot2)

ggplot(df_plot, aes(x = OR, y = variable)) +
  geom_point(size = 2) +
  geom_errorbarh(aes(xmin = OR_low, xmax = OR_high), height = 0.2) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +
  scale_x_log10() +
  labs(
    x = "Odds Ratio (log scale)",
    y = "",
    title = "Risk factors for CRKP carriage at admission"
  ) +
  theme_minimal(base_size = 12)

# Highlight
df_plot <- df_plot %>%
  mutate(significant = OR_low > 1 | OR_high < 1)

ggplot(df_plot, aes(x = OR, y = variable, color = significant)) +
  geom_point(size = 2) +
  geom_errorbarh(aes(xmin = OR_low, xmax = OR_high), height = 0.2) +
  geom_vline(xintercept = 1, linetype = "dashed") +
  scale_x_log10() +
  scale_color_manual(values = c("grey50", "blue")) +
  theme_minimal()

# export
ggsave("forest_plot_kp.png", width = 7, height = 6, dpi = 300)
```

# Escherichia coli

## Mixed-effect logistic regression

```{r}
Ec_dataset <- "Escherichia coli" |> 
make_data() |> 
as_tibble() |> 
na.exclude() |> 
mutate(across(where(~ !is.numeric(.x)), as.factor),
       age = as.numeric(scale(age)))

Ec_mixed_model <- glmer(carrier ~ age + GENDER + smoking + children + married + job + CORMOBIDITY + CPD + SEV_RENAL + DIAB_EOD + alcohol_problem + drug_problem + hospitaltype + wardtype + InvasiveHistory + MedicationHistory + HealthcareHistory + Ab_history + ICDGroup + (1 | SITEID),
                            Ec_dataset, binomial)
```

```{r}
summary(Ec_mixed_model)
```

For CREC, the random effect **SITEID is contributing** → the model is effectively **multilevel.**

**–\> include the random effect in brms model**

## Bayesian model in brms

### Check data distribution

```{r}
ggplot(make_data("Escherichia coli"), 
       aes(x = carrier)) +   
  geom_bar(fill = "skyblue", color = "black") +   
  labs(title = "Bernoulli Distribution of carriage status",        
       x = "Carriage (0 = No, 1 = Yes)",
       y = "Count") +   
  theme_minimal()   
```

### Prepare for brms model

```{r}
# check names exist
stopifnot(all(predictors_full %in% names(Ec_dataset)))

#quick check on missing
missing_summary <- Ec_dataset %>% select(all_of(c("carrier", predictors_full, "SITEID"))) %>% summarise(across(everything(), ~ mean(is.na(.))))
View(missing_summary)


# Construct model formula with covariates

Ec_dataset <- Ec_dataset %>% mutate(carrier01 = as.integer(carrier == "TRUE"))
formula_brm <- as.formula(paste0("carrier01 ~ ", rhs, " + (1 | SITEID)"))
```

### Run brms model with priors

```{r}
priors1 <- c(
  prior(normal(0, 1.5), class = "b"),        # coefficient shrinkage
  prior(normal(0, 1), class = "Intercept"),
  prior(student_t(3, 0, 2.5), class = "sd") # random intercept SD
)

Ec_brms_model <- brms::brm(formula = formula_brm,
                        Ec_dataset, family = bernoulli(link = "logit"),
                        prior = priors1, 
                        chains = 3,
                        cores = parallel::detectCores(),
                        iter = 3000,  
                        warmup = 1000,
                        control = list(adapt_delta = 0.99, max_treedepth = 15),
                        seed = 2026)

summary(Ec_brms_model) 
```

### Convergence check

```{r}
sampler_diagnostics <- nuts_params(Ec_brms_model)

summary(Ec_brms_model)$fixed
rhat(Ec_brms_model)
neff_ratio(Ec_brms_model)
```

### Model checks

```{r}
pp_check(Ec_brms_model, ndraws = 200)   # posterior predictive check

loo_model <- loo(Ec_brms_model, moment_match = FALSE)
print(loo_model)

print(bayes_R2(Ec_brms_model))
```

### Posterior summaries

```{r}
post_summary <- posterior_summary(Ec_brms_model)
post_summary[grep("^b_", rownames(post_summary)), , drop = FALSE]  # show coefficients

# Posterior draws
draws <- as_draws_df(Ec_brms_model)

# Extract fixed effects only
beta_draws <- draws %>% select(starts_with("b_"))

# Convert to odds ratios
or_draws <- exp(beta_draws)

# Posterior summaries (median + 95% CrI)
or_summary <- apply(or_draws, 2, function(x)
  c(
    median = median(x),
    l95 = quantile(x, 0.025),
    u95 = quantile(x, 0.975)
  )
)

t(or_summary)
```

### Forest Plot

```{r}
#prepare data

# Get posterior summary (log-odds)
post <- posterior_summary(Ec_brms_model)

# Keep only fixed effects
post <- post[grep("^b_", rownames(post)), ]

# Convert to data frame
df_plot <- as.data.frame(post) %>%
  rownames_to_column("variable") %>%
  mutate(
    variable = gsub("^b_", "", variable),

    # Convert to odds ratios
    OR = exp(Estimate),
    OR_low = exp(Q2.5),
    OR_high = exp(Q97.5)
  )

#Clean variable names
df_plot <- df_plot %>%
  mutate(variable = recode(variable,
    age = "Age",
    GENDERmale = "Male sex",
    smokingTRUE = "Smoking",
    childrenTRUE = "Children in household",
    marriedTRUE = "Married",
    independentTRUE = "Independent",
    jobfarmer = "Farmer",
    jobhousewife = "Housewife",
    jobretired = "Retired",
    CORMOBIDITYTRUE = "Comorbidity",
    vascular_diseaseTRUE = "Vascular disease",
    cancerTRUE = "Cancer",
    CPDTRUE = "Chronic pulmonary disease",
    CTDTRUE = "Connective tissue disease",
    PUDTRUE = "Peptic ulcer disease",
    MILD_LIVERTRUE = "Mild liver disease",
    SEV_LIVERTRUE = "Severe liver disease",
    HEMIPLEGIATRUE = "Hemiplegia",
    SEV_RENALTRUE = "Severe renal disease",
    DIAB_NOEODTRUE = "Diabetes (no EOD)",
    DIAB_EODTRUE = "Diabetes (EOD)",
    alcohol_problemTRUE = "Alcohol use problem",
    drug_problemTRUE = "Drug use problem",
    hospitaltypeprovincial = "Provincial hospital",
    wardtypesurgical = "Surgical ward",
    InvasiveHistoryTRUE = "Invasive procedure history",
    MedicationHistoryTRUE = "Medication history (not antibiotic)",
    HealthcareHistoryTRUE = "Prior hospitalization",
    Ab_historyTRUE = "Prior antibiotic use",
    ICDGroupDigestivediseases = "Digestive diseases diagnosis",
    ICDGroupGenitourinarydiseases = "Genitourinary diseases diagnosis",
    ICDGroupIDIntestinal = "Intestinal Infectious diseases diagnosis",
    ICDGroupIDOther = "Other Infectious diseases diagnosis",
    ICDGroupNeoplasms = "Neoplasms diagnosis",
    ICDGroupOther = "Other diagnosis",
    ICDGroupRespiratorydiseases = "Respiratory diseases diagnosis"
  ))

# Order variables
df_plot <- df_plot %>%
  arrange(desc(OR)) %>%
  mutate(variable = factor(variable, levels = variable))

# Create plot
library(ggplot2)

ggplot(df_plot, aes(x = OR, y = variable)) +
  geom_point(size = 2) +
  geom_errorbarh(aes(xmin = OR_low, xmax = OR_high), height = 0.2) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +
  scale_x_log10() +
  labs(
    x = "Odds Ratio (log scale)",
    y = "",
    title = "Risk factors for CREC carriage at admission"
  ) +
  theme_minimal(base_size = 12)

# Highlight
df_plot <- df_plot %>%
  mutate(significant = OR_low > 1 | OR_high < 1)

ggplot(df_plot, aes(x = OR, y = variable, color = significant)) +
  geom_point(size = 2) +
  geom_errorbarh(aes(xmin = OR_low, xmax = OR_high), height = 0.2) +
  geom_vline(xintercept = 1, linetype = "dashed") +
  scale_x_log10() +
  scale_color_manual(values = c("grey50", "blue")) +
  theme_minimal()

# export
ggsave("forest_plot_ecoli.png", width = 7, height = 6, dpi = 300)
```
